---
title: "Ladder with 10ys Duration"
output: html_document
author: "Hadi"
---

```{r}

library(arules)
library(arulesViz)
library(knitr)
library(dplyr)
library(RColorBrewer)
library(stringr)
library(quantmod)
library(splines2)
library(splines)
library(mgcv)
library(RQuantLib)
library(tidyr)
library(xts)
library(plotly)
library(lubridate)
library(readxl)
library(ggplot2)
library(scatterplot3d)
library(tidyverse)
library(zoo)
library(writexl)
library(YieldCurve)
library(patchwork)
library(gridExtra)
library(stargazer)
library(scales)
library(pdfetch)
library(xtable)
```

Load data sets
```{r}

California <- readRDS(need("/path/to/data" ))
MLFeat <- read_xlsx(need("/path/to/data" ))
ARL_S2 <- readRDS(need("/path/to/data" ))

par_data <- read_csv(need("daily_par_yield-curve-rates-1990-2024.csv"),
                       na = c("NA","#N/A N/A","#N/A Field Not Applicable","#N/A Invalid Security"))

names(par_data)[-1] <- c("0.083", "0.167", "0.231", "0.333", "0.500", "1", "2", "3",
"5", "7", "10", "20", "30")

par_data$Date <- as.Date(par_data$Date)

par_data_mat <- as.matrix(par_data)
par_data_mat <- par_data_mat[, -1]

par_tby <- as.xts(par_data_mat, order.by = par_data$Date)

par_tby <- na.approx(par_tby, na.rm = FALSE)


```


Bootstrapping Par yields
```{r}


# --- BOOTSTRAP ZERO RATES FROM PAR YIELDS ---

# Helper function: Get zero rate at specific time (with interpolation)
get_zero_for_time <- function(zero_rates, maturities, target_time, max_idx) {
  if (max_idx < 1) return(NA_real_)
  
  # Only use already-calculated rates
  avail_zeros <- zero_rates[1:max_idx]
  avail_mats <- maturities[1:max_idx]
  
  # Remove NAs
  valid <- !is.na(avail_zeros)
  if (!any(valid)) return(NA_real_)
  
  avail_zeros <- avail_zeros[valid]
  avail_mats <- avail_mats[valid]
  
  # Exact match
  exact <- which(abs(avail_mats - target_time) < 0.01)
  if (length(exact) > 0) return(avail_zeros[exact[1]])
  
  # Before first point
  if (target_time < min(avail_mats)) return(avail_zeros[1])
  
  # After last point
  if (target_time > max(avail_mats)) return(avail_zeros[length(avail_zeros)])
  
  # Linear interpolation
  lower <- max(which(avail_mats <= target_time))
  upper <- min(which(avail_mats >= target_time))
  
  t1 <- avail_mats[lower]
  t2 <- avail_mats[upper]
  z1 <- avail_zeros[lower]
  z2 <- avail_zeros[upper]
  
  weight <- (target_time - t1) / (t2 - t1)
  return(z1 + weight * (z2 - z1))
}

# Main bootstrap function
bootstrap_zero_correct <- function(yields, maturities) {
  n <- length(maturities)
  zero_rates <- rep(NA_real_, n)
  
  for (i in seq_len(n)) {
    if (is.na(yields[i])) next
    
    t <- maturities[i]
    par <- yields[i]
    
    # Keep short maturities (≤ 0.5 years) as par - these are T-Bills (zero coupon)
    if (i == 1 || t <= 0.5) {
      zero_rates[i] <- par
      next
    }
    
    # Check if we have any previous zero rates
    if (all(is.na(zero_rates[1:(i-1)]))) {
      zero_rates[i] <- par
      next
    }
    
    # For longer maturities (> 0.5 years), do full bootstrap
    coupon <- par / 2
    n_periods <- round(t * 2)
    
    # Discount ALL coupon payments (except the final one with principal)
    pv_coupons <- 0
    for (period in 1:(n_periods - 1)) {
      coupon_time <- period / 2
      z_rate <- get_zero_for_time(zero_rates, maturities, coupon_time, i - 1)
      
      if (!is.na(z_rate)) {
        pv_coupons <- pv_coupons + coupon / (1 + z_rate/200)^period
      }
    }
    
    # Solve for zero rate: 100 = pv_coupons + (100 + coupon) / (1 + z/2)^n
    final_payment <- 100 + coupon
    pv_final <- 100 - pv_coupons
    
    if (pv_final > 0) {
      z_semi <- (final_payment / pv_final)^(1/n_periods) - 1
      zero_rates[i] <- z_semi * 2 * 100
    } else {
      zero_rates[i] <- par  # Fallback
    }
  }
  
  return(zero_rates)
}

# --- MAIN CODE---

# Get all maturity columns (INCLUDING 0.333)
maturity_cols <- setdiff(names(par_data), "Date")
maturities <- as.numeric(maturity_cols)

# Sort by maturity
sorted_idx <- order(maturities)
maturities <- maturities[sorted_idx]
maturity_cols <- maturity_cols[sorted_idx]

# Prepare output dataframe
zero_data <- par_data[, c("Date", maturity_cols)]
zero_data[, maturity_cols] <- NA_real_

# Apply bootstrap for each date (row)
for (row in seq_len(nrow(par_data))) {
  yields <- as.numeric(par_data[row, maturity_cols])
  if (all(is.na(yields))) next
  
  zero_row <- bootstrap_zero_correct(yields, maturities)
  zero_data[row, maturity_cols] <- as.list(zero_row)
}




names(zero_data)[-1] <- c("0.083", "0.167", "0.231", "0.333", "0.500", "1", "2", "3",
"5", "7", "10", "20", "30")

zero_data$Date <- as.Date(zero_data$Date)

zero_data_mat <- as.matrix(zero_data)
zero_data_mat <- zero_data_mat[, -1]

zero_tby <- as.xts(zero_data_mat, order.by = zero_data$Date)

zero_tby <- na.approx(zero_tby, na.rm = FALSE)


```



Data preprocessing and Macaulay duration calculation
```{r}

#Preparing the dataset
California <- California %>%
  left_join(ARL_S2 %>% 
              distinct(ID_CUSIP, .keep_all = TRUE) %>%
              dplyr::select(ID_CUSIP, Iss_pri._spread, S_AT_Iss, DAM, DM, Y_OID,
                     log_AMT_ISSUED, Amt_iss_int, log_MUNI_ISSUE_SIZE, 
                     MUNI_ISSUE_SIZE_int, Log_DEBT, Log_Sale_Turn, 
                     MTY_YEARS_int, Y_l_day, Active_years, years_to_maturity, 
                     Active_years_int, years_to_maturity_int), 
            by = "ID_CUSIP")






# --- Function to calculate Macaulay Duration (using YF = years to maturity) ---
calc_macaulay_duration <- function(ytm, price, coupon_rate, freq, face = 100, years_to_maturity) {
  if (is.na(ytm) || is.na(price) || is.na(coupon_rate) || is.na(freq) ||
      is.na(years_to_maturity) || price <= 0 || years_to_maturity <= 0) return(NA)
  
  y <- ytm / 100 / freq                    # Yield per period
  c <- face * coupon_rate / 100 / freq     # Coupon payment per period
  n <- round(years_to_maturity * freq)     # Total number of payments
  
  t <- 1:n
  CF <- rep(c, n)
  CF[n] <- CF[n] + face                    # Add face value at maturity
  
  PV_CF <- CF / (1 + y)^t
  duration <- sum(t * PV_CF) / (freq * price)
  
  return(duration)
}

# --- Apply to California dataset ---
California <- California %>%
  rowwise() %>%
  mutate(
    duration_mac = calc_macaulay_duration(
      ytm = yield,
      price = GPV_2,
      coupon_rate = CPN,
      freq = CPN_FREQ,
      years_to_maturity = YF
    )
  ) %>%
  ungroup()

```

# ============================================================================
# GREEN BONDS PORTFOLIO WITH DYNAMIC DURATION-BASED TENOR SELECTION
# ============================================================================

```{r}

# ============================================================================
# SECTION 1: CREATE 9 CURVE-FITTING GROUPS 
# ============================================================================

# Callable and Non-callable Bond datasets
Cal_callable <- California %>% filter(CALLABLE == "TRUE", CPN != 15, CPN_FREQ != 12)
Cal_non_callable <- California %>% filter(CALLABLE == "FALSE", CPN != 15, CPN_FREQ != 12)

# Coupon intervals
interval_non_call <- cut(Cal_non_callable$CPN, breaks = c(0, 2.99, 4.999, 7.69), 
                         labels = c("CPN_0_3", "CPN_3_5", "CPN_5_8"))
Cal_non_callable <- Cal_non_callable %>% mutate(CPN_Group = interval_non_call)

interval_call <- cut(Cal_callable$CPN, breaks = c(0, 3.5, 4.999, 8.5), 
                     labels = c("CPN_0_3.5", "CPN_3.5_5", "CPN_5_8.5"))
Cal_callable <- Cal_callable %>% mutate(CPN_Group = interval_call)

# Tax provinces to EXCLUDE in the "op" groups
excluded_tax <- c(
  "FED TAXABLE/ST TAX-EXEMPT",
  "FED TAXABLE",
  "FED TAXABLE/ST TAXABLE"
)

# --------- NON-CALLABLE ---------
G1_nc_all <- Cal_non_callable %>%
  filter(
    CPN_Group == "CPN_0_3",
    Date >= as.Date("2020-01-01")
  )

G2_nc_op <- Cal_non_callable %>%
  filter(
    CPN_Group == "CPN_3_5",
    Date >= as.Date("2020-01-01"),
    !is.na(MUNI_TAX_PROV),
    !(MUNI_TAX_PROV %in% excluded_tax)    
  )

G2_nc_ft <- Cal_non_callable %>%
  filter(
    CPN_Group == "CPN_3_5",
    Date >= as.Date("2020-01-01"),
    MUNI_TAX_PROV == "FED TAXABLE/ST TAX-EXEMPT"
  )

G3_nc_all <- Cal_non_callable %>%
  filter(
    CPN_Group == "CPN_5_8",
    Date >= as.Date("2020-01-01")
  )

# --------- CALLABLE ---------
G1_c_op <- Cal_callable %>%
  filter(
    CPN_Group == "CPN_0_3.5",
    Date >= as.Date("2020-01-01"),
    !is.na(MUNI_TAX_PROV),
    !(MUNI_TAX_PROV %in% excluded_tax)     
  )

G1_c_ft <- Cal_callable %>%
  filter(
    CPN_Group == "CPN_0_3.5",
    Date >= as.Date("2020-01-01"),
    MUNI_TAX_PROV == "FED TAXABLE/ST TAX-EXEMPT"
  )

G2_c_op <- Cal_callable %>%
  filter(
    CPN_Group == "CPN_3.5_5",
    Date >= as.Date("2020-01-01"),
    !is.na(MUNI_TAX_PROV),
    !(MUNI_TAX_PROV %in% excluded_tax)     
  )

G2_c_ft <- Cal_callable %>%
  filter(
    CPN_Group == "CPN_3.5_5",
    Date >= as.Date("2020-01-01"),
    MUNI_TAX_PROV == "FED TAXABLE/ST TAX-EXEMPT"
  )

G3_c_all <- Cal_callable %>%
  filter(
    CPN_Group == "CPN_5_8.5",
    Date >= as.Date("2020-01-01"),
    !is.na(MUNI_TAX_PROV),
    !(MUNI_TAX_PROV %in% excluded_tax)    
  )

cat("\n=== Curve-Fitting Groups Created ===\n")
cat("G1_nc_all:", nrow(G1_nc_all), "bonds\n")
cat("G2_nc_op:", nrow(G2_nc_op), "bonds\n")
cat("G2_nc_ft:", nrow(G2_nc_ft), "bonds\n")
cat("G3_nc_all:", nrow(G3_nc_all), "bonds\n")
cat("G1_c_op:", nrow(G1_c_op), "bonds\n")
cat("G1_c_ft:", nrow(G1_c_ft), "bonds\n")
cat("G2_c_op:", nrow(G2_c_op), "bonds\n")
cat("G2_c_ft:", nrow(G2_c_ft), "bonds\n")
cat("G3_c_all:", nrow(G3_c_all), "bonds\n")


# ============================================================================
# HELPER FUNCTION: Identify which curve-fitting group a bond belongs to
# ============================================================================

identify_bond_group <- function(callable, cpn, tax_prov) {
  
  # Determine if callable
  is_callable <- (callable == "TRUE" | callable == TRUE | callable == "Callable")
  
  # Determine coupon group
  if (is_callable) {
    if (cpn <= 3.5) {
      cpn_group <- "CPN_0_3.5"
    } else if (cpn <= 5) {
      cpn_group <- "CPN_3.5_5"
    } else {
      cpn_group <- "CPN_5_8.5"
    }
  } else {
    if (cpn <= 3) {
      cpn_group <- "CPN_0_3"
    } else if (cpn <= 5) {
      cpn_group <- "CPN_3_5"
    } else {
      cpn_group <- "CPN_5_8"
    }
  }
  
  # Determine tax province group
  is_excluded_tax <- !is.na(tax_prov) && tax_prov %in% excluded_tax
  is_fed_taxable_st_exempt <- !is.na(tax_prov) && tax_prov == "FED TAXABLE/ST TAX-EXEMPT"
  
  # Match to specific group
  if (!is_callable) {
    # Non-callable
    if (cpn_group == "CPN_0_3") {
      return("G1_nc_all")
    } else if (cpn_group == "CPN_3_5") {
      if (is_fed_taxable_st_exempt) {
        return("G2_nc_ft")
      } else {
        return("G2_nc_op")
      }
    } else if (cpn_group == "CPN_5_8") {
      return("G3_nc_all")
    }
  } else {
    # Callable
    if (cpn_group == "CPN_0_3.5") {
      if (is_fed_taxable_st_exempt) {
        return("G1_c_ft")
      } else {
        return("G1_c_op")
      }
    } else if (cpn_group == "CPN_3.5_5") {
      if (is_fed_taxable_st_exempt) {
        return("G2_c_ft")
      } else {
        return("G2_c_op")
      }
    } else if (cpn_group == "CPN_5_8.5") {
      return("G3_c_all")
    }
  }
  
  return(NA)  # If no match found
}

# ============================================================================
# HELPER FUNCTION: Get the actual dataset for a group name 
# ============================================================================

get_group_data <- function(group_name) {
  switch(group_name,
         "G1_nc_all" = G1_nc_all,
         "G2_nc_op" = G2_nc_op,
         "G2_nc_ft" = G2_nc_ft,
         "G3_nc_all" = G3_nc_all,
         "G1_c_op" = G1_c_op,
         "G1_c_ft" = G1_c_ft,
         "G2_c_op" = G2_c_op,
         "G2_c_ft" = G2_c_ft,
         "G3_c_all" = G3_c_all,
         NULL)
}

# ============================================================================
# HELPER FUNCTIONS FOR ZERO-COUPON RATE CONVERSION 
# ============================================================================

# Function for calculating bond prices using fitted yields
bp_calculator_a2 <- function(x, y, m, cuts, bond_type, year_fraction, coupon_rate, 
                          coupon_frequency, face_value) {
  
  bond_price <- 0
  fitted_curve <- suppressWarnings(lm(y ~ bs(x, degree = m, knots = cuts)))
  
  if (bond_type %in% c("FIXED", "FIXED, OID")) {
    C <- face_value * coupon_rate / coupon_frequency
    n <- year_fraction * coupon_frequency
    tau_n <- c(seq(ifelse(n %% 1 == 0.00, 1, n %% 1), n, by = 1) / coupon_frequency)
    
    for (t in tau_n) {
      discounted_cashflow <- 
        C / ((1 + predict(fitted_curve, newdata = data.frame(x = t))/(100*coupon_frequency)) ^ which(tau_n == t))
      bond_price <- bond_price + discounted_cashflow 
    }
    
    final_cashflow <- 
      (face_value) / ((1 + predict(fitted_curve, newdata = data.frame(x = year_fraction))/(100*coupon_frequency)) ^ which(tau_n == year_fraction))
    bond_price <- bond_price + final_cashflow  
  } else if (bond_type == "ZERO COUPON") {
    bond_price <- 
      (face_value) / ((1 + predict(fitted_curve, newdata = data.frame(x = year_fraction))/(100*coupon_frequency)) ^ which(tau_n == year_fraction))
  } else {
    stop("Unsupported bond type")
  }
  
  return(bond_price)
}

# Function for calculating equivalent ZCB YTM (EQ.10)
zcb_eq_YTM_2 <- function(zcb_ytm, year_fraction,
                           face_value, bond_type, bond_price, 
                          coupon, coupon_frequency) {
  C <- face_value * coupon / coupon_frequency
  n <- year_fraction * coupon_frequency
  tau_n <- c(seq(ifelse(n %% 1 == 0.00, 1, n %% 1), n, by = 1) / coupon_frequency)
  if (bond_type %in% c("FIXED", "FIXED, OID", "ZERO COUPON, OID")) {
    return(((1 + zcb_ytm) ^ which(tau_n == year_fraction)) - ((face_value + C) / bond_price))
  } else {
    stop("Unsupported bond_type")
  }
}

# ============================================================================
# HELPER FUNCTION: Extract ZERO-COUPON yield using appropriate group 
# ============================================================================

extract_zcb_yield_safe <- function(current_date, target_tenor, 
                                    bond_callable, bond_cpn, bond_tax_prov,
                                    min_yield = -5, max_yield = 15,
                                    outlier_threshold = 1000,
                                    coupon_frequency = 2, face_value = 100) {
  
  # Identify which group this bond belongs to
  group_name <- identify_bond_group(bond_callable, bond_cpn, bond_tax_prov)
  
  if (is.na(group_name)) {
    return(list(zcb_yield = NA, flag = "NO_GROUP_MATCH", n_bonds = 0, group = NA))
  }
  
  # Get the appropriate group data
  group_data <- get_group_data(group_name)
  
  if (is.null(group_data) || nrow(group_data) == 0) {
    return(list(zcb_yield = NA, flag = "EMPTY_GROUP", n_bonds = 0, group = group_name))
  }
  
  # Get bonds available on this date from the group
  bonds_today <- group_data %>%
    filter(Date == current_date)
  
  # CHECK 1: Need at least 5 bonds for reliable curve fitting
  if (nrow(bonds_today) < 5) {
    return(list(zcb_yield = NA, flag = "INSUFFICIENT_DATA", n_bonds = nrow(bonds_today), group = group_name))
  }
  
  # CHECK 2: Is target tenor within data range?
  tenor_range <- range(bonds_today$YF, na.rm = TRUE)
  
  if (target_tenor < tenor_range[1] || target_tenor > tenor_range[2]) {
    closest_tenor <- ifelse(target_tenor < tenor_range[1], 
                            tenor_range[1], 
                            tenor_range[2])
    flag <- paste0("EXTRAPOLATION_AVOIDED: Used tenor ", round(closest_tenor, 2), 
                   " instead of ", round(target_tenor, 2))
    target_tenor <- closest_tenor
  } else {
    flag <- "OK"
  }
  
  # Fit curve
  tryCatch({
    x <- bonds_today$YF
    y <- bonds_today$yield
    
    # CHECK 3: Remove outlier yields before fitting
    y_median <- median(y, na.rm = TRUE)
    y_mad <- mad(y, na.rm = TRUE)
    outliers <- abs(y - y_median) > outlier_threshold * y_mad
    
    if (sum(outliers) > 0) {
      x <- x[!outliers]
      y <- y[!outliers]
      flag <- paste0(flag, " | OUTLIERS_REMOVED:", sum(outliers))
    }
    
    # Recheck after outlier removal
    if (length(x) < 3) {
      return(list(zcb_yield = NA, flag = "INSUFFICIENT_DATA_AFTER_CLEANING", 
                  n_bonds = length(x), group = group_name))
    }
    
    # Fit the curve
    m <- 1
    cuts <- summary(sort(x))[c(2, 3, 5)]
    
    # STEP 1: Calculate bond price using fitted coupon bond yields
    typical_coupon <- median(y, na.rm = TRUE) / 100
    
    bond_price <- bp_calculator_a2(
      x = x, 
      y = y, 
      m = m, 
      cuts = cuts,
      bond_type = "FIXED",
      year_fraction = target_tenor,
      coupon_rate = typical_coupon,
      coupon_frequency = coupon_frequency,
      face_value = face_value
    )
    
    # STEP 2: Convert to equivalent zero-coupon yield
    zcb_yield_result <- tryCatch({
      uniroot(
        f = zcb_eq_YTM_2,
        interval = c(-0.10, 0.30),
        year_fraction = target_tenor,
        face_value = face_value,
        bond_type = "FIXED",
        bond_price = bond_price,
        coupon = typical_coupon,
        coupon_frequency = coupon_frequency
      )$root
    }, error = function(e) {
      return((face_value / bond_price)^(1/(target_tenor * coupon_frequency)) - 1)
    })
    
    # Convert to percentage
    zcb_yield_pct <- zcb_yield_result * 100
    
    # CHECK 4: Bound yields to reasonable range
    original_yield <- zcb_yield_pct
    zcb_yield_pct <- pmax(min_yield, pmin(max_yield, zcb_yield_pct))
    
    if (abs(original_yield - zcb_yield_pct) > 0.01) {
      flag <- paste0(flag, " | YIELD_CAPPED: ", round(original_yield, 2), 
                     "% -> ", round(zcb_yield_pct, 2), "%")
    }
    
    return(list(
      zcb_yield = zcb_yield_pct,
      flag = flag,
      n_bonds = length(x),
      group = group_name
    ))
    
  }, error = function(e) {
    return(list(zcb_yield = NA, flag = paste("ERROR:", e$message), 
                n_bonds = nrow(bonds_today), group = group_name))
  })
}

# ============================================================================
# HELPER FUNCTION: Find nearest trading date 
# ============================================================================

find_nearest_trading_date <- function(target_date, available_dates) {
  date_diffs <- abs(as.numeric(available_dates - target_date))
  nearest_idx <- which.min(date_diffs)
  return(available_dates[nearest_idx])
}

# ============================================================================
# HELPER FUNCTION: Calculate Macaulay Duration for a bond
# ============================================================================

calculate_bond_duration <- function(ytm, coupon_rate, years_to_maturity, 
                                    coupon_frequency = 2, face_value = 100) {
  
  # Calculate number of periods
  n_periods <- years_to_maturity * coupon_frequency
  
  # Coupon payment per period
  C <- (coupon_rate / 100) * face_value / coupon_frequency
  
  # Discount rate per period
  r <- (ytm / 100) / coupon_frequency
  
  # Calculate weighted present value of cash flows
  weighted_pv <- 0
  total_pv <- 0
  
  for (t in 1:n_periods) {
    time_years <- t / coupon_frequency
    pv_cashflow <- C / (1 + r)^t
    weighted_pv <- weighted_pv + (time_years * pv_cashflow)
    total_pv <- total_pv + pv_cashflow
  }
  
  # Add final payment (principal)
  pv_principal <- face_value / (1 + r)^n_periods
  weighted_pv <- weighted_pv + (years_to_maturity * pv_principal)
  total_pv <- total_pv + pv_principal
  
  # Macaulay duration
  duration <- weighted_pv / total_pv
  
  return(duration)
}

# ============================================================================
# HELPER FUNCTION: Find bond with target duration (WITH TENOR CONSTRAINTS)
# ============================================================================

find_bond_with_target_duration <- function(purchase_data, 
                                           current_date, 
                                           target_duration,
                                           synthetic_callable,
                                           synthetic_coupon,
                                           synthetic_tax_prov,
                                           duration_tolerance = 2.0,
                                           min_tenor = 5.0,
                                           max_tenor = 20.0) {
  
  # Get bonds available on this date that match synthetic bond characteristics
  available_bonds <- purchase_data %>%
    filter(Date == current_date,
           CALLABLE == synthetic_callable,
           MUNI_TAX_PROV == synthetic_tax_prov,
           !is.na(duration_mac),
           !is.na(YF),
           !is.na(yield))
  
  if (nrow(available_bonds) == 0) {
    return(list(
      tenor = NA,
      duration = NA,
      yield = NA,
      n_candidates = 0,
      status = "NO_BONDS_AVAILABLE"
    ))
  }
  
  n_total_candidates <- nrow(available_bonds)
  
  # APPLY TENOR CONSTRAINTS: Filter out bonds with tenor < min_tenor or > max_tenor
  available_bonds <- available_bonds %>%
    filter(YF >= min_tenor, YF <= max_tenor)
  
  n_after_tenor_filter <- nrow(available_bonds)
  
  if (nrow(available_bonds) == 0) {
    return(list(
      tenor = NA,
      duration = NA,
      yield = NA,
      n_candidates = n_total_candidates,
      n_after_tenor_filter = 0,
      status = "NO_BONDS_IN_TENOR_RANGE",
      message = paste0("All ", n_total_candidates, " candidates outside tenor range [", 
                      min_tenor, ", ", max_tenor, "]")
    ))
  }
  
  # Calculate distance from target duration
  available_bonds <- available_bonds %>%
    mutate(duration_diff = abs(duration_mac - target_duration))
  
  # Find bonds with closest duration
  min_diff <- min(available_bonds$duration_diff, na.rm = TRUE)
  
  # Check if the closest match is within tolerance
  if (min_diff > duration_tolerance) {
    return(list(
      tenor = NA,
      duration = NA,
      yield = NA,
      n_candidates = n_total_candidates,
      n_after_tenor_filter = n_after_tenor_filter,
      status = "NO_GOOD_MATCH",
      min_diff = min_diff,
      message = paste0(n_after_tenor_filter, " bonds in tenor range, but closest duration diff = ", 
                      round(min_diff, 2), " > tolerance ", duration_tolerance)
    ))
  }
  
  closest_bonds <- available_bonds %>%
    filter(duration_diff == min_diff)
  
  # If multiple bonds with same duration, pick the one with higher yield
  if (nrow(closest_bonds) > 1) {
    selected_bond <- closest_bonds %>%
      arrange(desc(yield)) %>%
      slice(1)
  } else {
    selected_bond <- closest_bonds
  }
  
  return(list(
    tenor = selected_bond$YF[1],
    duration = selected_bond$duration_mac[1],
    yield = selected_bond$yield[1],
    n_candidates = n_total_candidates,
    n_after_tenor_filter = n_after_tenor_filter,
    status = "GOOD_MATCH",
    cusip = selected_bond$ID_CUSIP[1],
    message = paste0("Found match from ", n_after_tenor_filter, " bonds in tenor range [", 
                    min_tenor, ", ", max_tenor, "]")
  ))
}

# ============================================================================
# HELPER FUNCTION: Calculate portfolio duration
# ============================================================================

calculate_portfolio_duration <- function(bond_positions, 
                                        current_date,
                                        current_index,
                                        bond_values,
                                        new_bond_value = 0,
                                        new_bond_duration = 0) {
  
  if (length(bond_positions) == 0 && new_bond_value == 0) {
    return(0)
  }
  
  total_value <- sum(bond_values, na.rm = TRUE) + new_bond_value
  
  if (total_value == 0) {
    return(0)
  }
  
  weighted_duration <- 0
  
  # Existing bonds
  for (j in 1:length(bond_positions)) {
    bond <- bond_positions[[j]]
    
    if (bond$purchase_date > current_date) {
      next
    }
    
    # Calculate remaining tenor
    days_held <- as.numeric(current_date - bond$purchase_date)
    years_held <- days_held / 365
    remaining_tenor <- bond$purchase_tenor - years_held
    
    if (remaining_tenor > 0 && !is.na(bond_values[j]) && bond_values[j] > 0) {
      
      # Calculate duration for this bond
      bond_duration <- calculate_bond_duration(
        ytm = bond$purchase_zcb_yield,
        coupon_rate = bond$cpn,
        years_to_maturity = remaining_tenor,
        coupon_frequency = 2,
        face_value = 100
      )
      
      weight <- bond_values[j] / total_value
      weighted_duration <- weighted_duration + (weight * bond_duration)
    }
  }
  
  # New bond
  if (new_bond_value > 0) {
    weight <- new_bond_value / total_value
    weighted_duration <- weighted_duration + (weight * new_bond_duration)
  }
  
  return(weighted_duration)
}

# ============================================================================
# HELPER FUNCTION: Calculate required duration for new bond
# ============================================================================

calculate_required_duration <- function(current_portfolio_duration,
                                       current_portfolio_value,
                                       new_bond_value,
                                       target_portfolio_duration) {
  
  total_value <- current_portfolio_value + new_bond_value
  
  if (total_value == 0) {
    return(target_portfolio_duration)
  }
  
  # Weighted average formula:
  # target_duration = (current_duration * current_value + new_duration * new_value) / total_value
  # Solve for new_duration:
  
  required_duration <- (target_portfolio_duration * total_value - 
                       current_portfolio_duration * current_portfolio_value) / new_bond_value
  
  return(required_duration)
}

# ============================================================================
# HELPER FUNCTION: Convert duration to approximate tenor
# ============================================================================

duration_to_tenor <- function(target_duration, coupon_rate = 2.5, ytm = 2.5) {
  
  approx_tenor <- target_duration * (1 + ytm/200)
  return(approx_tenor)
}

# ============================================================================
# MAIN FUNCTION: Portfolio Construction with Dynamic Duration-Based Tenor Selection
# FINAL REVISION: Added tenor constraints (5-20 years)
# ============================================================================

construct_portfolio_zcb_synthetic_duration <- function(purchase_data,  
                                                       par_data,
                                                       w0 = 1000000,           
                                                       alpha = 0.10,           
                                                       start_date = "2020-01-01",
                                                       end_date = "2024-12-31",
                                                       r_f_annual = 0.01,
                                                       target_portfolio_duration = 10.0,
                                                       min_target_duration = 9.0,
                                                       max_target_duration = 11.0,
                                                       min_price = 20,
                                                       max_price = 150,
                                                       max_daily_price_change = 0.10,
                                                       max_daily_portfolio_change = 0.20,
                                                       coupon_frequency = 2,
                                                       face_value = 100,
                                                       duration_match_tolerance = 2.0,
                                                       min_tenor = 5.0,
                                                       max_tenor = 20.0) {
  
  # Calculate median coupon from purchase_data to determine synthetic bond coupon
  median_coupon <- median(purchase_data$CPN, na.rm = TRUE)
  synthetic_coupon <- round(median_coupon * 2) / 2  # Round to nearest 0.5
  
  # Synthetic bond characteristics (fixed for all purchases)
  synthetic_callable <- "FALSE"
  
  # Determine most prevalent tax province in purchase_data based on unique CUSIPs
  tax_prov_counts <- purchase_data %>%
    group_by(MUNI_TAX_PROV) %>%
    summarise(n_cusips = n_distinct(ID_CUSIP), .groups = 'drop') %>%
    arrange(desc(n_cusips))
  
  synthetic_tax_prov <- tax_prov_counts$MUNI_TAX_PROV[1]
  
  cat("\n=== Tax Province Selection ===\n")
  cat("Tax province counts in purchase_data:\n")
  print(tax_prov_counts)
  cat("\nSelected tax province:", synthetic_tax_prov, 
      "(", tax_prov_counts$n_cusips[1], "unique CUSIPs )\n")
  
  # Determine which group this synthetic bond belongs to
  synthetic_group <- identify_bond_group(
    callable = synthetic_callable,
    cpn = synthetic_coupon,
    tax_prov = synthetic_tax_prov
  )
  
  cat("\n=== Synthetic Bond Configuration ===\n")
  cat("Target Portfolio Duration:", target_portfolio_duration, "years\n")
  cat("Duration Range:", min_target_duration, "-", max_target_duration, "years\n")
  cat("Coupon:", synthetic_coupon, "% (median from purchase_data:", round(median_coupon, 2), "%)\n")
  cat("Callable:", synthetic_callable, "\n")
  cat("Tax Status:", synthetic_tax_prov, "\n")
  cat("Assigned Curve Group:", synthetic_group, "\n")
  cat("Duration Match Tolerance:", duration_match_tolerance, "years\n")
  cat("Tenor Constraints: [", min_tenor, ", ", max_tenor, "] years\n\n", sep = "")
  
  # Get all trading dates
  all_dates <- par_data %>%
    filter(Date >= as.Date(start_date) & Date <= as.Date(end_date)) %>%
    pull(Date)
  
  # Create SCHEDULED purchase dates (every 6 months)
  scheduled_purchase_dates <- seq(as.Date(start_date), as.Date(end_date), by = "6 months")
  
  # Map to ACTUAL trading dates
  actual_purchase_dates <- sapply(scheduled_purchase_dates, function(target) {
    find_nearest_trading_date(target, all_dates)
  })
  actual_purchase_dates <- as.Date(actual_purchase_dates, origin = "1970-01-01")
  
  cat("=== Purchase Schedule ===\n")
  purchase_schedule <- data.frame(
    Scheduled = scheduled_purchase_dates,
    Actual = actual_purchase_dates,
    Days_Diff = as.numeric(actual_purchase_dates - scheduled_purchase_dates)
  )
  print(purchase_schedule)
  cat("Total scheduled purchases:", length(scheduled_purchase_dates), "\n\n")
  
  # Initialize tracking
  cash_account <- rep(NA, length(all_dates))
  cash_account[1] <- w0
  bond_positions <- list()
  purchased_info <- rep(NA_character_, length(all_dates))
  
  # Duration tracking
  portfolio_duration_history <- rep(NA, length(all_dates))
  target_duration_history <- rep(NA, length(all_dates))
  
  # Logging data frame
  daily_log <- data.frame(
    Date = all_dates,
    n_bonds_held = 0,
    flags = "",
    zcb_yield_used = NA,
    group_used = NA_character_,
    price_capped = FALSE,
    abnormal_price_fixed = FALSE,
    portfolio_change_pct = NA,
    portfolio_duration = NA,
    target_duration = NA
  )
  
  # Store last valid prices BY BOND
  last_valid_prices <- list()
  bonds_purchased <- character()
  
  # Daily rate calculation
  daily_rate <- (1 + r_f_annual)^(1/365) - 1
  
  # ========== PURCHASE LOOP WITH DYNAMIC DURATION-BASED TENOR SELECTION ==========
  
  for (i in 1:length(all_dates)) {
    current_date <- all_dates[i]
    
    # --- PURCHASE LOGIC: Create synthetic bond with duration-based tenor ---
    if (current_date %in% actual_purchase_dates && 
        !as.character(current_date) %in% bonds_purchased) {
      
      bonds_purchased <- c(bonds_purchased, as.character(current_date))
      
      is_first_purchase <- (length(bond_positions) == 0)
      
      if (is_first_purchase) {
        cat("\n=== FIRST PURCHASE ===\n")
        cat("Date:", format(current_date, "%Y-%m-%d"), "\n")
        
        # For first purchase: find bond with duration closest to target (10 years)
        bond_match <- find_bond_with_target_duration(
          purchase_data = purchase_data,
          current_date = current_date,
          target_duration = target_portfolio_duration,
          synthetic_callable = synthetic_callable,
          synthetic_coupon = synthetic_coupon,
          synthetic_tax_prov = synthetic_tax_prov,
          duration_tolerance = duration_match_tolerance,
          min_tenor = min_tenor,
          max_tenor = max_tenor
        )
        
        if (!is.na(bond_match$tenor)) {
          # Good match found
          synthetic_tenor <- bond_match$tenor
          cat("Target Duration:", target_portfolio_duration, "years\n")
          cat("Matched Duration:", round(bond_match$duration, 2), "years\n")
          cat("Selected Tenor (YF):", round(synthetic_tenor, 2), "years\n")
          cat("Matched Yield:", round(bond_match$yield, 2), "%\n")
          cat("Total Candidates:", bond_match$n_candidates, "\n")
          cat("After Tenor Filter:", bond_match$n_after_tenor_filter, "\n")
          cat("Status: MATCHED FROM DATA\n")
          cat(bond_match$message, "\n")
        } else {
          # No good match - use fallback (10-year tenor)
          synthetic_tenor <- target_portfolio_duration
          
          # Convert duration to approximate tenor for better estimation
          synthetic_tenor <- duration_to_tenor(target_portfolio_duration, 
                                               coupon_rate = synthetic_coupon)
          
          # Ensure fallback tenor is within bounds
          synthetic_tenor <- pmax(min_tenor, pmin(max_tenor, synthetic_tenor))
          
          cat("Target Duration:", target_portfolio_duration, "years\n")
          cat("WARNING: No bonds within tolerance\n")
          cat("Total Candidates:", bond_match$n_candidates, "\n")
          if (!is.null(bond_match$n_after_tenor_filter)) {
            cat("After Tenor Filter:", bond_match$n_after_tenor_filter, "\n")
          }
          cat("Status:", bond_match$status, "\n")
          if (!is.null(bond_match$message)) {
            cat(bond_match$message, "\n")
          }
          cat("Using FALLBACK tenor:", round(synthetic_tenor, 2), "years (constrained to [", 
              min_tenor, ", ", max_tenor, "])\n", sep = "")
        }
        
      } else {
        cat("\n=== SUBSEQUENT PURCHASE #", length(bond_positions) + 1, "===\n")
        cat("Date:", format(current_date, "%Y-%m-%d"), "\n")
        
        # Calculate current portfolio value and duration
        current_bond_values <- rep(0, length(bond_positions))
        
        for (j in 1:length(bond_positions)) {
          bond <- bond_positions[[j]]
          
          if (bond$purchase_date > current_date) {
            next
          }
          
          days_held <- as.numeric(current_date - bond$purchase_date)
          years_held <- days_held / 365
          remaining_tenor <- bond$purchase_tenor - years_held
          
          if (remaining_tenor > 0) {
            # Get cached price
            cache_key <- paste0("bond_", bond$bond_id)
            current_price <- last_valid_prices[[cache_key]]
            if (is.null(current_price)) {
              current_price <- bond$purchase_price
            }
            current_bond_values[j] <- bond$units * current_price
          }
        }
        
        current_portfolio_value <- sum(current_bond_values, na.rm = TRUE)
        
        # Calculate current portfolio duration (without new bond)
        current_portfolio_duration <- calculate_portfolio_duration(
          bond_positions = bond_positions,
          current_date = current_date,
          current_index = i,
          bond_values = current_bond_values,
          new_bond_value = 0,
          new_bond_duration = 0
        )
        
        cat("Current Portfolio Value: $", round(current_portfolio_value, 2), "\n")
        cat("Current Portfolio Duration:", round(current_portfolio_duration, 2), "years\n")
        
        # Calculate required duration for new bond
        new_bond_value <- alpha * w0
        required_duration <- calculate_required_duration(
          current_portfolio_duration = current_portfolio_duration,
          current_portfolio_value = current_portfolio_value,
          new_bond_value = new_bond_value,
          target_portfolio_duration = target_portfolio_duration
        )
        
        cat("Required New Bond Duration:", round(required_duration, 2), "years\n")
        
        # Handle edge cases for required duration
        if (required_duration <= 0) {
          cat("WARNING: Required duration is non-positive. Using default (10 years).\n")
          required_duration <- 10.0
        }
        
        if (required_duration > 30) {
          cat("WARNING: Required duration very high (", round(required_duration, 2), 
              "). Capping at 30 years.\n")
          required_duration <- 30.0
        }
        
        # Try to find bond with target duration
        bond_match <- find_bond_with_target_duration(
          purchase_data = purchase_data,
          current_date = current_date,
          target_duration = required_duration,
          synthetic_callable = synthetic_callable,
          synthetic_coupon = synthetic_coupon,
          synthetic_tax_prov = synthetic_tax_prov,
          duration_tolerance = duration_match_tolerance,
          min_tenor = min_tenor,
          max_tenor = max_tenor
        )
        
        if (!is.na(bond_match$tenor)) {
          # Good match found
          synthetic_tenor <- bond_match$tenor
          cat("Matched Duration:", round(bond_match$duration, 2), "years\n")
          cat("Selected Tenor (YF):", round(synthetic_tenor, 2), "years\n")
          cat("Matched Yield:", round(bond_match$yield, 2), "%\n")
          cat("Total Candidates:", bond_match$n_candidates, "\n")
          cat("After Tenor Filter:", bond_match$n_after_tenor_filter, "\n")
          cat("Status: MATCHED FROM DATA\n")
          cat(bond_match$message, "\n")
        } else {
          # No good match - use calculated required duration as tenor
          # Convert duration to approximate tenor
          synthetic_tenor <- duration_to_tenor(required_duration, 
                                               coupon_rate = synthetic_coupon)
          
          # Ensure fallback tenor is within bounds
          synthetic_tenor <- pmax(min_tenor, pmin(max_tenor, synthetic_tenor))
          
          cat("WARNING: No bonds within tolerance\n")
          cat("Total Candidates:", bond_match$n_candidates, "\n")
          if (!is.null(bond_match$n_after_tenor_filter)) {
            cat("After Tenor Filter:", bond_match$n_after_tenor_filter, "\n")
          }
          cat("Status:", bond_match$status, "\n")
          if (!is.null(bond_match$message)) {
            cat(bond_match$message, "\n")
          }
          cat("Using CALCULATED REQUIRED DURATION as tenor:", round(synthetic_tenor, 2), 
              "years (constrained to [", min_tenor, ", ", max_tenor, "])\n", sep = "")
        }
      }
      
      # Extract ZERO-COUPON yield using the synthetic bond's GROUP
      zcb_result <- extract_zcb_yield_safe(
        current_date = current_date,
        target_tenor = synthetic_tenor,
        bond_callable = synthetic_callable,
        bond_cpn = synthetic_coupon,
        bond_tax_prov = synthetic_tax_prov,
        coupon_frequency = coupon_frequency,
        face_value = face_value
      )
      
      purchase_zcb_yield <- zcb_result$zcb_yield
      group_used <- zcb_result$group
      
      if (!is.na(purchase_zcb_yield)) {
        # Calculate price using ZERO-COUPON formula
        purchase_price <- face_value / (1 + purchase_zcb_yield/100)^synthetic_tenor
        purchase_price <- pmax(min_price, pmin(max_price, purchase_price))
        
        units <- (alpha * w0) / purchase_price
        
        # Create synthetic bond position
        new_bond <- data.frame(
          bond_id = length(bond_positions) + 1,
          purchase_date = current_date,
          purchase_index = i,
          purchase_tenor = synthetic_tenor,
          units = units,
          face_value = face_value,
          maturity_date = current_date + years(ceiling(synthetic_tenor)),
          purchase_price = purchase_price,
          purchase_zcb_yield = purchase_zcb_yield,
          cusip = paste0("SYNTHETIC_", format(current_date, "%Y%m%d")),
          callable = synthetic_callable,
          cpn = synthetic_coupon,
          tax_prov = synthetic_tax_prov,
          curve_group = group_used
        )
        
        bond_positions[[length(bond_positions) + 1]] <- new_bond
        
        # Initialize price cache for this bond
        cache_key <- paste0("bond_", new_bond$bond_id)
        last_valid_prices[[cache_key]] <- purchase_price
        
        purchased_info[i] <- paste0("Synthetic Bond #", new_bond$bond_id, 
                                    " | CUSIP: ", new_bond$cusip, 
                                    " | Tenor: ", round(synthetic_tenor, 2),
                                    " | Coupon: ", synthetic_coupon, "%",
                                    " | ZCB Yield: ", round(purchase_zcb_yield, 2), "%",
                                    " | Price: $", round(purchase_price, 2),
                                    " | Group: ", group_used)
        
        # Deduct from cash
        cash_account[i] <- cash_account[i] - (alpha * w0)
        
        cat("Purchase Confirmed: ", purchased_info[i], "\n")
      } else {
        cat("ERROR: Could not extract yield for synthetic bond on", 
            format(current_date, "%Y-%m-%d"),
            "- Group:", group_used, "- Flag:", zcb_result$flag, "\n")
      }
    }
    
    # --- CASH COMPOUNDING ---
    if (i < length(all_dates)) {
      cash_account[i + 1] <- cash_account[i] * (1 + daily_rate)
    }
  }
  
  cat("\n=== Purchase Summary ===\n")
  cat("Total synthetic bonds purchased:", length(bond_positions), "\n")
  cat("Expected purchases:", length(scheduled_purchase_dates), "\n\n")
  
  # ========== VALUATION LOOP WITH DURATION TRACKING ==========
  
  portfolio_value <- rep(NA, length(all_dates))
  bond_value_daily <- rep(0, length(all_dates))
  
  for (i in 1:length(all_dates)) {
    current_date <- all_dates[i]
    
    portfolio_value[i] <- cash_account[i]
    total_bond_value <- 0
    all_flags <- character()
    n_active_bonds <- 0
    
    # Track bond values for duration calculation
    current_bond_values <- rep(0, length(bond_positions))
    
    if (length(bond_positions) > 0) {
      
      for (j in 1:length(bond_positions)) {
        bond <- bond_positions[[j]]
        
        if (bond$purchase_date > current_date) {
          next
        }
        
        # Calculate remaining tenor
        days_held <- as.numeric(current_date - bond$purchase_date)
        years_held <- days_held / 365
        remaining_tenor <- bond$purchase_tenor - years_held
        
        if (remaining_tenor > 0) {
          
          n_active_bonds <- n_active_bonds + 1
          
          # Extract ZERO-COUPON yield using bond's GROUP
          zcb_result <- extract_zcb_yield_safe(
            current_date = current_date,
            target_tenor = remaining_tenor,
            bond_callable = bond$callable,
            bond_cpn = bond$cpn,
            bond_tax_prov = bond$tax_prov,
            coupon_frequency = coupon_frequency,
            face_value = face_value
          )
          
          tenor_zcb_yield <- zcb_result$zcb_yield
          flag <- zcb_result$flag
          group_used <- zcb_result$group
          
          # Get previous day's price for this bond
          cache_key <- paste0("bond_", bond$bond_id)
          previous_price <- last_valid_prices[[cache_key]]
          if (is.null(previous_price)) {
            previous_price <- bond$purchase_price
          }
          
          # Calculate new price
          if (!is.na(tenor_zcb_yield)) {
            # Calculate price using ZERO-COUPON formula
            calculated_price <- face_value / (1 + tenor_zcb_yield/100)^remaining_tenor
            
            # ABNORMAL PRICE CHECK #1: Is calculated price within absolute bounds?
            if (calculated_price < min_price || calculated_price > max_price) {
              current_price <- previous_price
              daily_log$abnormal_price_fixed[i] <- TRUE
              all_flags <- c(all_flags, paste0("Bond", bond$bond_id, ":PRICE_BOUNDS_", 
                                               round(calculated_price, 2)))
            } else {
              # ABNORMAL PRICE CHECK #2: Is daily change reasonable?
              price_change_pct <- abs(calculated_price - previous_price) / previous_price
              
              if (price_change_pct > max_daily_price_change) {
                # Price changed too much - use previous price
                current_price <- previous_price
                daily_log$abnormal_price_fixed[i] <- TRUE
                all_flags <- c(all_flags, paste0("Bond", bond$bond_id, ":ABNORMAL_CHANGE_", 
                                                 round(price_change_pct * 100, 1), "%"))
              } else {
                # Price is reasonable
                current_price <- calculated_price
                
                # Update cache
                last_valid_prices[[cache_key]] <- current_price
                
                # Store yield (first bond's info)
                if (is.na(daily_log$zcb_yield_used[i])) {
                  daily_log$zcb_yield_used[i] <- tenor_zcb_yield
                  daily_log$group_used[i] <- group_used
                }
              }
            }
          } else {
            # No valid yield - use previous price
            current_price <- previous_price
            all_flags <- c(all_flags, paste0("Bond", bond$bond_id, ":", flag))
          }
          
          bond_value <- bond$units * current_price
          current_bond_values[j] <- bond_value
          total_bond_value <- total_bond_value + bond_value
        }
      }
      
      bond_value_daily[i] <- total_bond_value
      portfolio_value[i] <- portfolio_value[i] + total_bond_value
      
      # Calculate portfolio duration
      portfolio_duration <- calculate_portfolio_duration(
        bond_positions = bond_positions,
        current_date = current_date,
        current_index = i,
        bond_values = current_bond_values,
        new_bond_value = 0,
        new_bond_duration = 0
      )
      
      portfolio_duration_history[i] <- portfolio_duration
      target_duration_history[i] <- target_portfolio_duration
      
      daily_log$portfolio_duration[i] <- portfolio_duration
      daily_log$target_duration[i] <- target_portfolio_duration
    }
    
    # Store logging info
    daily_log$n_bonds_held[i] <- n_active_bonds
    if (length(all_flags) > 0) {
      daily_log$flags[i] <- paste(all_flags, collapse = "; ")
    }
    
    # Calculate portfolio change
    if (i > 1 && !is.na(portfolio_value[i-1]) && portfolio_value[i-1] > 0) {
      pct_change <- (portfolio_value[i] - portfolio_value[i-1]) / portfolio_value[i-1]
      daily_log$portfolio_change_pct[i] <- pct_change * 100
      
      # Flag abnormal portfolio changes
      if (abs(pct_change) > max_daily_portfolio_change) {
        daily_log$flags[i] <- paste0(daily_log$flags[i], 
                                     " | ABNORMAL_PORTFOLIO_CHANGE:", 
                                     round(pct_change * 100, 1), "%")
      }
    }
  }
  
  # ========== CREATE FINAL PORTFOLIO DATAFRAME ==========
  
  portfolio_df <- data.frame(
    Date = all_dates,
    Cash = cash_account,
    Bonds = bond_value_daily,
    Portfolio_Value = portfolio_value,
    Portfolio_Duration = portfolio_duration_history,
    Target_Duration = target_duration_history,
    N_Bonds = daily_log$n_bonds_held
  )
  
  # Calculate returns
  portfolio_df <- portfolio_df %>%
    mutate(
      Daily_Return = (Portfolio_Value / lag(Portfolio_Value) - 1) * 100,
      Cumulative_Return = (Portfolio_Value / w0 - 1) * 100
    )
  
  # ========== SUMMARY STATISTICS ==========
  
  final_value <- portfolio_value[length(portfolio_value)]
  total_return <- (final_value / w0 - 1) * 100
  
  cat("\n=== Portfolio Performance Summary ===\n")
  cat("Initial Capital: $", format(w0, big.mark = ","), "\n", sep = "")
  cat("Final Portfolio Value: $", format(round(final_value, 2), big.mark = ","), "\n", sep = "")
  cat("Total Return: ", round(total_return, 2), "%\n", sep = "")
  cat("Final Cash: $", format(round(cash_account[length(cash_account)], 2), big.mark = ","), "\n", sep = "")
  cat("Final Bond Value: $", format(round(bond_value_daily[length(bond_value_daily)], 2), big.mark = ","), "\n", sep = "")
  cat("Average Portfolio Duration: ", round(mean(portfolio_duration_history, na.rm = TRUE), 2), " years\n", sep = "")
  cat("Target Portfolio Duration: ", target_portfolio_duration, " years\n", sep = "")
  
  # ========== CREATE PLOTS ==========
  
  cat("\n=== Generating Plots ===\n")
  
  # 1. Duration Plot
  duration_plot <- ggplot(portfolio_df %>% filter(!is.na(Portfolio_Duration)), 
                         aes(x = Date)) +
    geom_line(aes(y = Portfolio_Duration, color = "Actual Duration"), size = 1) +
    geom_hline(aes(yintercept = target_portfolio_duration, color = "Target Duration"), 
               linetype = "dashed", size = 1) +
    geom_ribbon(aes(ymin = min_target_duration, ymax = max_target_duration), 
                alpha = 0.2, fill = "blue") +
    scale_color_manual(name = "Duration", 
                      values = c("Actual Duration" = "darkblue", 
                                "Target Duration" = "red")) +
    labs(title = "Portfolio Duration Over Time",
         subtitle = paste0("Target: ", target_portfolio_duration, " years (Range: ", 
                          min_target_duration, "-", max_target_duration, " years) | Tenor Constraints: [", 
                          min_tenor, ", ", max_tenor, "] years"),
         x = "Date",
         y = "Duration (Years)") +
    theme_minimal() +
    theme(legend.position = "bottom",
          plot.title = element_text(face = "bold", size = 14))
  
  print(duration_plot)
  
  # 2. Portfolio Value Plot
  portfolio_value_plot <- ggplot(portfolio_df, aes(x = Date)) +
    geom_line(aes(y = Portfolio_Value, color = "Total Portfolio"), size = 1.2) +
    geom_line(aes(y = Bonds, color = "Bond Value"), size = 1) +
    geom_line(aes(y = Cash, color = "Cash"), size = 1) +
    geom_hline(yintercept = w0, linetype = "dashed", color = "gray50", size = 0.8) +
    scale_color_manual(name = "Component", 
                      values = c("Total Portfolio" = "black", 
                                "Bond Value" = "darkgreen", 
                                "Cash" = "steelblue")) +
    scale_y_continuous(labels = scales::dollar) +
    labs(title = "Portfolio Value Over Time",
         subtitle = "Green Bonds Portfolio with Dynamic Duration-Based Tenor Selection",
         x = "Date",
         y = "Value ($)") +
    theme_minimal() +
    theme(legend.position = "bottom",
          plot.title = element_text(face = "bold", size = 14))
  
  print(portfolio_value_plot)
  

  
  # 3. Daily Return Distribution Plot
  daily_return_plot <- ggplot(portfolio_df %>% filter(!is.na(Daily_Return)), 
                             aes(x = Daily_Return)) +
    geom_histogram(aes(y = ..density..), bins = 50, fill = "steelblue", alpha = 0.7) +
    geom_density(color = "darkblue", size = 1) +
    geom_vline(xintercept = 0, linetype = "dashed", color = "red") +
    labs(title = "Daily Return Distribution",
         subtitle = paste0("Mean: ", round(mean(portfolio_df$Daily_Return, na.rm = TRUE), 3), 
                          "% | SD: ", round(sd(portfolio_df$Daily_Return, na.rm = TRUE), 3), "%"),
         x = "Daily Return (%)",
         y = "Density") +
    theme_minimal() +
    theme(plot.title = element_text(face = "bold", size = 14))
  
  print(daily_return_plot)
  
  # ========== RETURN RESULTS ==========
  
  return(list(
    portfolio = portfolio_df,
    bond_positions = bond_positions,
    daily_log = daily_log,
    purchase_info = data.frame(
      Date = all_dates,
      Info = purchased_info
    ) %>% filter(!is.na(Info)),
    duration_plot = duration_plot,
    portfolio_value_plot = portfolio_value_plot,
    return_plot = return_plot,
    daily_return_plot = daily_return_plot,
    summary = list(
      initial_capital = w0,
      final_value = final_value,
      total_return_pct = total_return,
      avg_duration = mean(portfolio_duration_history, na.rm = TRUE),
      target_duration = target_portfolio_duration,
      n_bonds_purchased = length(bond_positions),
      final_cash = cash_account[length(cash_account)],
      final_bonds = bond_value_daily[length(bond_value_daily)],
      tenor_constraints = c(min_tenor, max_tenor)
    )
  ))
}


```
# ============================================================================
# Green bonds Example (Test)
# ============================================================================
```{r}

cat("\n" , rep("=", 80), "\n")
cat("EXECUTING GREEN BONDS PORTFOLIO WITH DYNAMIC DURATION-BASED TENOR SELECTION\n")
cat("FINAL REVISION: Added tenor constraints (5-20 years)\n")
cat(rep("=", 80), "\n\n")


# ============================================================================
# CREATE PURCHASE GROUPS 
# ============================================================================

# Rule 1: Tax status and non-callable (for purchasing)
rule1_data <- California %>%
  filter(MUNI_TAX_PROV %in% c("FED TAXABLE/ST TAX-EXEMPT"),
         CALLABLE == "FALSE")

cat("\n=== Purchase Groups Created ===\n")
cat("rule1_data:", nrow(rule1_data), "bonds\n")



green_bonds_result <- construct_portfolio_zcb_synthetic_duration(
  purchase_data = rule1_data,
  par_data = par_data,
  w0 = 1000000,
  alpha = 0.10,
  start_date = "2020-01-01",
  end_date = "2024-12-31",
  r_f_annual = 0.01,
  target_portfolio_duration = 10.0,
  min_target_duration = 9.0,
  max_target_duration = 11.0,
  min_price = 70,
  max_price = 120,
  max_daily_price_change = 0.10,
  coupon_frequency = 2,
  face_value = 100,
  duration_match_tolerance = 2.0,
  min_tenor = 5.0,
  max_tenor = 20.0
)

# Access results
cat("\n=== Results Available ===\n")
cat("green_bonds_result$portfolio - Portfolio values and returns over time\n")
cat("green_bonds_result$bond_positions - List of all bond purchases\n")
cat("green_bonds_result$daily_log - Detailed daily logs\n")
cat("green_bonds_result$purchase_info - Purchase information\n")
cat("green_bonds_result$duration_plot - Duration plot\n")
cat("green_bonds_result$portfolio_value_plot - Portfolio value plot\n")
cat("green_bonds_result$return_plot - Cumulative return plot\n")
cat("green_bonds_result$daily_return_plot - Daily return distribution\n")
cat("green_bonds_result$summary - Summary statistics\n")

# View portfolio head
cat("\n=== Portfolio Data (First 10 Rows) ===\n")
print(head(green_bonds_result$portfolio, 10))

# View purchase info
cat("\n=== Purchase Information ===\n")
print(green_bonds_result$purchase_info)

# Print summary
cat("\n=== Summary Statistics ===\n")
print(green_bonds_result$summary)

cat("\n" , rep("=", 80), "\n")
cat("GREEN BONDS PORTFOLIO CONSTRUCTION COMPLETE\n")
cat(rep("=", 80), "\n\n")


```

# ============================================================================
# TREASURY BONDS PORTFOLIO WITH DYNAMIC DURATION-BASED TENOR SELECTION
# ============================================================================


```{r}

# ============================================================================
# HELPER FUNCTION: Find nearest trading date (UNCHANGED)
# ============================================================================

find_nearest_trading_date <- function(target_date, available_dates) {
  date_diffs <- abs(as.numeric(available_dates - target_date))
  nearest_idx <- which.min(date_diffs)
  return(available_dates[nearest_idx])
}

# ============================================================================
# HELPER FUNCTION: Get Treasury rate for a specific tenor on a specific date
# ============================================================================

get_treasury_rate <- function(zero_tby_data, current_date, target_tenor) {
  # zero_tby columns: "0.083", "0.167", "0.231", "0.333", "0.500", "1", "2", "3",
  #                  "5", "7", "10", "20", "30"
  
  # Get available tenors
  available_tenors <- as.numeric(colnames(zero_tby_data))
  
  # Find closest tenor to target
  tenor_diff <- abs(available_tenors - target_tenor)
  closest_idx <- which.min(tenor_diff)
  closest_tenor <- available_tenors[closest_idx]
  
  # Get rate for this date
  date_index <- which(index(zero_tby_data) == current_date)
  
  if (length(date_index) == 0) {
    return(list(rate = NA, tenor_used = NA, status = "DATE_NOT_FOUND"))
  }
  
  rate <- as.numeric(zero_tby_data[date_index, closest_idx])
  
  if (is.na(rate)) {
    return(list(rate = NA, tenor_used = closest_tenor, status = "RATE_NA"))
  }
  
  return(list(
    rate = rate,
    tenor_used = closest_tenor,
    status = "OK"
  ))
}

# ============================================================================
# HELPER FUNCTION: Calculate portfolio duration for Treasury bonds
# ============================================================================

calculate_treasury_portfolio_duration <- function(bond_positions, 
                                                  current_date,
                                                  bond_values) {
  
  if (length(bond_positions) == 0) {
    return(0)
  }
  
  total_value <- sum(bond_values, na.rm = TRUE)
  
  if (total_value == 0) {
    return(0)
  }
  
  weighted_duration <- 0
  
  # For Treasury zero-coupon bonds, duration = remaining maturity
  for (j in 1:length(bond_positions)) {
    bond <- bond_positions[[j]]
    
    if (bond$purchase_date > current_date) {
      next
    }
    
    # Calculate remaining tenor (duration)
    days_held <- as.numeric(current_date - bond$purchase_date)
    years_held <- days_held / 365
    remaining_tenor <- bond$purchase_tenor - years_held
    
    if (remaining_tenor > 0 && !is.na(bond_values[j]) && bond_values[j] > 0) {
      # For zero-coupon bonds: duration = maturity
      bond_duration <- remaining_tenor
      
      weight <- bond_values[j] / total_value
      weighted_duration <- weighted_duration + (weight * bond_duration)
    }
  }
  
  return(weighted_duration)
}

# ============================================================================
# HELPER FUNCTION: Calculate required duration for new bond
# ============================================================================

calculate_required_duration <- function(current_portfolio_duration,
                                       current_portfolio_value,
                                       new_bond_value,
                                       target_portfolio_duration) {
  
  total_value <- current_portfolio_value + new_bond_value
  
  if (total_value == 0) {
    return(target_portfolio_duration)
  }
  
  # Weighted average formula:
  # target_duration = (current_duration * current_value + new_duration * new_value) / total_value
  # Solve for new_duration:
  
  required_duration <- (target_portfolio_duration * total_value - 
                       current_portfolio_duration * current_portfolio_value) / new_bond_value
  
  return(required_duration)
}

# ============================================================================
# HELPER FUNCTION: Select Treasury tenor based on target duration with constraints
# ============================================================================

select_treasury_tenor <- function(target_duration,
                                  available_tenors = c(0.083, 0.167, 0.231, 0.333, 0.5, 
                                                      1, 2, 3, 5, 7, 10, 20, 30),
                                  min_tenor = 5.0,
                                  max_tenor = 20.0) {
  
  # Filter tenors within constraints
  valid_tenors <- available_tenors[available_tenors >= min_tenor & available_tenors <= max_tenor]
  
  if (length(valid_tenors) == 0) {
    # No valid tenors - return closest to target within overall range
    if (target_duration < min_tenor) {
      return(list(tenor = min_tenor, status = "CAPPED_AT_MIN"))
    } else if (target_duration > max_tenor) {
      return(list(tenor = max_tenor, status = "CAPPED_AT_MAX"))
    } else {
      return(list(tenor = target_duration, status = "NO_VALID_TENORS"))
    }
  }
  
  # Find closest valid tenor to target
  tenor_diff <- abs(valid_tenors - target_duration)
  closest_idx <- which.min(tenor_diff)
  selected_tenor <- valid_tenors[closest_idx]
  
  return(list(
    tenor = selected_tenor,
    status = "OK",
    n_valid_tenors = length(valid_tenors)
  ))
}

# ============================================================================
# MAIN FUNCTION: Treasury Portfolio Construction with Duration-Based Tenor Selection
# ============================================================================

construct_treasury_portfolio_duration <- function(zero_tby_data,
                                                  w0 = 1000000,
                                                  alpha = 0.10,
                                                  start_date = "2020-01-01",
                                                  end_date = "2024-12-31",
                                                  r_f_annual = 0.01,
                                                  target_portfolio_duration = 10.0,
                                                  min_target_duration = 9.0,
                                                  max_target_duration = 11.0,
                                                  min_price = 20,
                                                  max_price = 150,
                                                  max_daily_price_change = 0.10,
                                                  max_daily_portfolio_change = 0.20,
                                                  face_value = 100,
                                                  min_tenor = 5.0,
                                                  max_tenor = 20.0) {
  
  cat("\n=== Treasury Bond Portfolio Configuration ===\n")
  cat("Target Portfolio Duration:", target_portfolio_duration, "years\n")
  cat("Duration Range:", min_target_duration, "-", max_target_duration, "years\n")
  cat("Tenor Constraints: [", min_tenor, ", ", max_tenor, "] years\n", sep = "")
  cat("Note: Treasury bonds are zero-coupon, so Duration = Maturity\n\n")
  
  # Get all trading dates
  all_dates <- index(zero_tby_data)
  all_dates <- all_dates[all_dates >= as.Date(start_date) & all_dates <= as.Date(end_date)]
  
  # Create SCHEDULED purchase dates (every 6 months)
  scheduled_purchase_dates <- seq(as.Date(start_date), as.Date(end_date), by = "6 months")
  
  # Map to ACTUAL trading dates
  actual_purchase_dates <- sapply(scheduled_purchase_dates, function(target) {
    find_nearest_trading_date(target, all_dates)
  })
  actual_purchase_dates <- as.Date(actual_purchase_dates, origin = "1970-01-01")
  
  cat("=== Purchase Schedule ===\n")
  purchase_schedule <- data.frame(
    Scheduled = scheduled_purchase_dates,
    Actual = actual_purchase_dates,
    Days_Diff = as.numeric(actual_purchase_dates - scheduled_purchase_dates)
  )
  print(purchase_schedule)
  cat("Total scheduled purchases:", length(scheduled_purchase_dates), "\n\n")
  
  # Initialize tracking
  cash_account <- rep(NA, length(all_dates))
  cash_account[1] <- w0
  bond_positions <- list()
  purchased_info <- rep(NA_character_, length(all_dates))
  
  # Duration tracking
  portfolio_duration_history <- rep(NA, length(all_dates))
  target_duration_history <- rep(NA, length(all_dates))
  
  # Logging data frame
  daily_log <- data.frame(
    Date = all_dates,
    n_bonds_held = 0,
    flags = "",
    treasury_rate_used = NA,
    price_capped = FALSE,
    abnormal_price_fixed = FALSE,
    portfolio_change_pct = NA,
    portfolio_duration = NA,
    target_duration = NA
  )
  
  # Store last valid prices BY BOND
  last_valid_prices <- list()
  bonds_purchased <- character()
  
  # Daily rate calculation
  daily_rate <- (1 + r_f_annual)^(1/365) - 1
  
  # ========== PURCHASE LOOP WITH DYNAMIC DURATION-BASED TENOR SELECTION ==========
  
  for (i in 1:length(all_dates)) {
    current_date <- all_dates[i]
    
    # --- PURCHASE LOGIC: Create Treasury bond with duration-based tenor ---
    if (current_date %in% actual_purchase_dates && 
        !as.character(current_date) %in% bonds_purchased) {
      
      bonds_purchased <- c(bonds_purchased, as.character(current_date))
      
      is_first_purchase <- (length(bond_positions) == 0)
      
      if (is_first_purchase) {
        cat("\n=== FIRST PURCHASE ===\n")
        cat("Date:", format(current_date, "%Y-%m-%d"), "\n")
        cat("Target Duration:", target_portfolio_duration, "years\n")
        
        # For first purchase: select tenor closest to target duration (10 years)
        # Since duration = maturity for zero-coupon bonds
        tenor_selection <- select_treasury_tenor(
          target_duration = target_portfolio_duration,
          min_tenor = min_tenor,
          max_tenor = max_tenor
        )
        
        selected_tenor <- tenor_selection$tenor
        
        cat("Selected Tenor:", selected_tenor, "years\n")
        cat("Status:", tenor_selection$status, "\n")
        if (!is.null(tenor_selection$n_valid_tenors)) {
          cat("Valid Tenors Available:", tenor_selection$n_valid_tenors, "\n")
        }
        
      } else {
        cat("\n=== SUBSEQUENT PURCHASE #", length(bond_positions) + 1, "===\n")
        cat("Date:", format(current_date, "%Y-%m-%d"), "\n")
        
        # Calculate current portfolio value and duration
        current_bond_values <- rep(0, length(bond_positions))
        
        for (j in 1:length(bond_positions)) {
          bond <- bond_positions[[j]]
          
          if (bond$purchase_date > current_date) {
            next
          }
          
          days_held <- as.numeric(current_date - bond$purchase_date)
          years_held <- days_held / 365
          remaining_tenor <- bond$purchase_tenor - years_held
          
          if (remaining_tenor > 0) {
            # Get cached price
            cache_key <- paste0("bond_", bond$bond_id)
            current_price <- last_valid_prices[[cache_key]]
            if (is.null(current_price)) {
              current_price <- bond$purchase_price
            }
            current_bond_values[j] <- bond$units * current_price
          }
        }
        
        current_portfolio_value <- sum(current_bond_values, na.rm = TRUE)
        
        # Calculate current portfolio duration (without new bond)
        current_portfolio_duration <- calculate_treasury_portfolio_duration(
          bond_positions = bond_positions,
          current_date = current_date,
          bond_values = current_bond_values
        )
        
        cat("Current Portfolio Value: $", round(current_portfolio_value, 2), "\n")
        cat("Current Portfolio Duration:", round(current_portfolio_duration, 2), "years\n")
        
        # Calculate required duration for new bond
        new_bond_value <- alpha * w0
        required_duration <- calculate_required_duration(
          current_portfolio_duration = current_portfolio_duration,
          current_portfolio_value = current_portfolio_value,
          new_bond_value = new_bond_value,
          target_portfolio_duration = target_portfolio_duration
        )
        
        cat("Required New Bond Duration:", round(required_duration, 2), "years\n")
        
        # Handle edge cases for required duration
        if (required_duration <= 0) {
          cat("WARNING: Required duration is non-positive. Using default (10 years).\n")
          required_duration <- 10.0
        }
        
        if (required_duration > 30) {
          cat("WARNING: Required duration very high (", round(required_duration, 2), 
              "). Capping at 30 years.\n")
          required_duration <- 30.0
        }
        
        # Select Treasury tenor based on required duration
        # For Treasury bonds: duration = maturity
        tenor_selection <- select_treasury_tenor(
          target_duration = required_duration,
          min_tenor = min_tenor,
          max_tenor = max_tenor
        )
        
        selected_tenor <- tenor_selection$tenor
        
        cat("Selected Tenor:", selected_tenor, "years\n")
        cat("Status:", tenor_selection$status, "\n")
        if (!is.null(tenor_selection$n_valid_tenors)) {
          cat("Valid Tenors Available:", tenor_selection$n_valid_tenors, "\n")
        }
      }
      
      # Get Treasury rate for selected tenor
      rate_result <- get_treasury_rate(
        zero_tby_data = zero_tby_data,
        current_date = current_date,
        target_tenor = selected_tenor
      )
      
      if (!is.na(rate_result$rate)) {
        # Treasury rate is already zero rate
        treasury_rate <- rate_result$rate
        tenor_used <- rate_result$tenor_used
        
        # Calculate price using zero-coupon formula
        # P = Face / (1 + r)^T
        purchase_price <- face_value / (1 + treasury_rate/100)^tenor_used
        purchase_price <- pmax(min_price, pmin(max_price, purchase_price))
        
        units <- (alpha * w0) / purchase_price
        
        # Create Treasury bond position
        new_bond <- data.frame(
          bond_id = length(bond_positions) + 1,
          purchase_date = current_date,
          purchase_index = i,
          purchase_tenor = tenor_used,
          units = units,
          face_value = face_value,
          maturity_date = current_date + years(ceiling(tenor_used)),
          purchase_price = purchase_price,
          purchase_rate = treasury_rate,
          cusip = paste0("TREASURY_", format(current_date, "%Y%m%d"))
        )
        
        bond_positions[[length(bond_positions) + 1]] <- new_bond
        
        # Initialize price cache for this bond
        cache_key <- paste0("bond_", new_bond$bond_id)
        last_valid_prices[[cache_key]] <- purchase_price
        
        purchased_info[i] <- paste0("Treasury Bond #", new_bond$bond_id, 
                                    " | CUSIP: ", new_bond$cusip, 
                                    " | Tenor: ", round(tenor_used, 2),
                                    " | Rate: ", round(treasury_rate, 2), "%",
                                    " | Price: $", round(purchase_price, 2))
        
        # Deduct from cash
        cash_account[i] <- cash_account[i] - (alpha * w0)
        
        cat("Purchase Confirmed: ", purchased_info[i], "\n")
      } else {
        cat("ERROR: Could not get Treasury rate for tenor", selected_tenor, "on", 
            format(current_date, "%Y-%m-%d"), "- Status:", rate_result$status, "\n")
      }
    }
    
    # --- CASH COMPOUNDING ---
    if (i < length(all_dates)) {
      cash_account[i + 1] <- cash_account[i] * (1 + daily_rate)
    }
  }
  
  cat("\n=== Purchase Summary ===\n")
  cat("Total Treasury bonds purchased:", length(bond_positions), "\n")
  cat("Expected purchases:", length(scheduled_purchase_dates), "\n\n")
  
  # ========== VALUATION LOOP WITH DURATION TRACKING ==========
  
  portfolio_value <- rep(NA, length(all_dates))
  bond_value_daily <- rep(0, length(all_dates))
  
  for (i in 1:length(all_dates)) {
    current_date <- all_dates[i]
    
    portfolio_value[i] <- cash_account[i]
    total_bond_value <- 0
    all_flags <- character()
    n_active_bonds <- 0
    
    # Track bond values for duration calculation
    current_bond_values <- rep(0, length(bond_positions))
    
    if (length(bond_positions) > 0) {
      
      for (j in 1:length(bond_positions)) {
        bond <- bond_positions[[j]]
        
        if (bond$purchase_date > current_date) {
          next
        }
        
        # Calculate remaining tenor
        days_held <- as.numeric(current_date - bond$purchase_date)
        years_held <- days_held / 365
        remaining_tenor <- bond$purchase_tenor - years_held
        
        if (remaining_tenor > 0) {
          
          n_active_bonds <- n_active_bonds + 1
          
          # Get current Treasury rate for remaining tenor
          rate_result <- get_treasury_rate(
            zero_tby_data = zero_tby_data,
            current_date = current_date,
            target_tenor = remaining_tenor
          )
          
          # Get previous day's price for this bond
          cache_key <- paste0("bond_", bond$bond_id)
          previous_price <- last_valid_prices[[cache_key]]
          if (is.null(previous_price)) {
            previous_price <- bond$purchase_price
          }
          
          # Calculate new price
          if (!is.na(rate_result$rate)) {
            # Calculate price using zero-coupon formula
            calculated_price <- face_value / (1 + rate_result$rate/100)^rate_result$tenor_used
            
            # ABNORMAL PRICE CHECK #1: Is calculated price within absolute bounds?
            if (calculated_price < min_price || calculated_price > max_price) {
              current_price <- previous_price
              daily_log$abnormal_price_fixed[i] <- TRUE
              all_flags <- c(all_flags, paste0("Bond", bond$bond_id, ":PRICE_BOUNDS_", 
                                               round(calculated_price, 2)))
            } else {
              # ABNORMAL PRICE CHECK #2: Is daily change reasonable?
              price_change_pct <- abs(calculated_price - previous_price) / previous_price
              
              if (price_change_pct > max_daily_price_change) {
                # Price changed too much - use previous price
                current_price <- previous_price
                daily_log$abnormal_price_fixed[i] <- TRUE
                all_flags <- c(all_flags, paste0("Bond", bond$bond_id, ":ABNORMAL_CHANGE_", 
                                                 round(price_change_pct * 100, 1), "%"))
              } else {
                # Price is reasonable
                current_price <- calculated_price
                
                # Update cache
                last_valid_prices[[cache_key]] <- current_price
                
                # Store rate (first bond's info)
                if (is.na(daily_log$treasury_rate_used[i])) {
                  daily_log$treasury_rate_used[i] <- rate_result$rate
                }
              }
            }
          } else {
            # No valid rate - use previous price
            current_price <- previous_price
            all_flags <- c(all_flags, paste0("Bond", bond$bond_id, ":", rate_result$status))
          }
          
          bond_value <- bond$units * current_price
          current_bond_values[j] <- bond_value
          total_bond_value <- total_bond_value + bond_value
        }
      }
      
      bond_value_daily[i] <- total_bond_value
      portfolio_value[i] <- portfolio_value[i] + total_bond_value
      
      # Calculate portfolio duration (for Treasury: duration = weighted average maturity)
      portfolio_duration <- calculate_treasury_portfolio_duration(
        bond_positions = bond_positions,
        current_date = current_date,
        bond_values = current_bond_values
      )
      
      portfolio_duration_history[i] <- portfolio_duration
      target_duration_history[i] <- target_portfolio_duration
      
      daily_log$portfolio_duration[i] <- portfolio_duration
      daily_log$target_duration[i] <- target_portfolio_duration
    }
    
    # Store logging info
    daily_log$n_bonds_held[i] <- n_active_bonds
    if (length(all_flags) > 0) {
      daily_log$flags[i] <- paste(all_flags, collapse = "; ")
    }
    
    # Calculate portfolio change
    if (i > 1 && !is.na(portfolio_value[i-1]) && portfolio_value[i-1] > 0) {
      pct_change <- (portfolio_value[i] - portfolio_value[i-1]) / portfolio_value[i-1]
      daily_log$portfolio_change_pct[i] <- pct_change * 100
      
      # Flag abnormal portfolio changes
      if (abs(pct_change) > max_daily_portfolio_change) {
        daily_log$flags[i] <- paste0(daily_log$flags[i], 
                                     " | ABNORMAL_PORTFOLIO_CHANGE:", 
                                     round(pct_change * 100, 1), "%")
      }
    }
  }
  
  # ========== CREATE FINAL PORTFOLIO DATAFRAME ==========
  
  portfolio_df <- data.frame(
    Date = all_dates,
    Cash = cash_account,
    Bonds = bond_value_daily,
    Portfolio_Value = portfolio_value,
    Portfolio_Duration = portfolio_duration_history,
    Target_Duration = target_duration_history,
    N_Bonds = daily_log$n_bonds_held
  )
  
  # Calculate returns
  portfolio_df <- portfolio_df %>%
    mutate(
      Daily_Return = (Portfolio_Value / lag(Portfolio_Value) - 1) * 100,
      Cumulative_Return = (Portfolio_Value / w0 - 1) * 100
    )
  
  # ========== SUMMARY STATISTICS ==========
  
  final_value <- portfolio_value[length(portfolio_value)]
  total_return <- (final_value / w0 - 1) * 100
  
  cat("\n=== Portfolio Performance Summary ===\n")
  cat("Initial Capital: $", format(w0, big.mark = ","), "\n", sep = "")
  cat("Final Portfolio Value: $", format(round(final_value, 2), big.mark = ","), "\n", sep = "")
  cat("Total Return: ", round(total_return, 2), "%\n", sep = "")
  cat("Final Cash: $", format(round(cash_account[length(cash_account)], 2), big.mark = ","), "\n", sep = "")
  cat("Final Bond Value: $", format(round(bond_value_daily[length(bond_value_daily)], 2), big.mark = ","), "\n", sep = "")
  cat("Average Portfolio Duration: ", round(mean(portfolio_duration_history, na.rm = TRUE), 2), " years\n", sep = "")
  cat("Target Portfolio Duration: ", target_portfolio_duration, " years\n", sep = "")
  
  # ========== CREATE PLOTS ==========
  
  cat("\n=== Generating Plots ===\n")
  
  # 1. Duration Plot
  duration_plot <- ggplot(portfolio_df %>% filter(!is.na(Portfolio_Duration)), 
                         aes(x = Date)) +
    geom_line(aes(y = Portfolio_Duration, color = "Actual Duration"), size = 1) +
    geom_hline(aes(yintercept = target_portfolio_duration, color = "Target Duration"), 
               linetype = "dashed", size = 1) +
    geom_ribbon(aes(ymin = min_target_duration, ymax = max_target_duration), 
                alpha = 0.2, fill = "blue") +
    scale_color_manual(name = "Duration", 
                      values = c("Actual Duration" = "darkblue", 
                                "Target Duration" = "red")) +
    labs(title = "Treasury Portfolio Duration Over Time",
         subtitle = paste0("Target: ", target_portfolio_duration, " years (Range: ", 
                          min_target_duration, "-", max_target_duration, " years) | Tenor Constraints: [", 
                          min_tenor, ", ", max_tenor, "] years"),
         x = "Date",
         y = "Duration (Years)") +
    theme_minimal() +
    theme(legend.position = "bottom",
          plot.title = element_text(face = "bold", size = 14))
  
  print(duration_plot)
  
  #2. Portfolio Value Plot
  portfolio_value_plot <- ggplot(portfolio_df, aes(x = Date)) +
    geom_line(aes(y = Portfolio_Value, color = "Total Portfolio"), size = 1.2) +
    geom_line(aes(y = Bonds, color = "Bond Value"), size = 1) +
    geom_line(aes(y = Cash, color = "Cash"), size = 1) +
    geom_hline(yintercept = w0, linetype = "dashed", color = "gray50", size = 0.8) +
    scale_color_manual(name = "Component",
                      values = c("Total Portfolio" = "black",
                                "Bond Value" = "darkgreen",
                                "Cash" = "steelblue")) +
    scale_y_continuous(labels = scales::dollar) +
    labs(title = "Treasury Portfolio Value Over Time",
         subtitle = "Treasury Bonds with Dynamic Duration-Based Tenor Selection",
         x = "Date",
         y = "Value ($)") +
    theme_minimal() +
    theme(legend.position = "bottom",
          plot.title = element_text(face = "bold", size = 14))

  print(portfolio_value_plot)
  
  # 3. Cumulative Return Plot
  return_plot <- ggplot(portfolio_df %>% filter(!is.na(Cumulative_Return)), 
                       aes(x = Date, y = Cumulative_Return)) +
    geom_line(color = "darkgreen", size = 1.2) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
    labs(title = "Cumulative Treasury Portfolio Return Over Time",
         subtitle = paste0("Total Return: ", round(total_return, 2), "%"),
         x = "Date",
         y = "Cumulative Return (%)") +
    theme_minimal() +
    theme(plot.title = element_text(face = "bold", size = 14))
  
  print(return_plot)
  
  # 4. Daily Return Distribution Plot
  daily_return_plot <- ggplot(portfolio_df %>% filter(!is.na(Daily_Return)), 
                             aes(x = Daily_Return)) +
    geom_histogram(aes(y = ..density..), bins = 50, fill = "steelblue", alpha = 0.7) +
    geom_density(color = "darkblue", size = 1) +
    geom_vline(xintercept = 0, linetype = "dashed", color = "red") +
    labs(title = "Daily Return Distribution - Treasury Portfolio",
         subtitle = paste0("Mean: ", round(mean(portfolio_df$Daily_Return, na.rm = TRUE), 3), 
                          "% | SD: ", round(sd(portfolio_df$Daily_Return, na.rm = TRUE), 3), "%"),
         x = "Daily Return (%)",
         y = "Density") +
    theme_minimal() +
    theme(plot.title = element_text(face = "bold", size = 14))
  
  print(daily_return_plot)
  
  # ========== RETURN RESULTS ==========
  
  return(list(
    portfolio = portfolio_df,
    bond_positions = bond_positions,
    daily_log = daily_log,
    purchase_info = data.frame(
      Date = all_dates,
      Info = purchased_info
    ) %>% filter(!is.na(Info)),
    duration_plot = duration_plot,
    portfolio_value_plot = portfolio_value_plot,
    return_plot = return_plot,
    daily_return_plot = daily_return_plot,
    summary = list(
      initial_capital = w0,
      final_value = final_value,
      total_return_pct = total_return,
      avg_duration = mean(portfolio_duration_history, na.rm = TRUE),
      target_duration = target_portfolio_duration,
      n_bonds_purchased = length(bond_positions),
      final_cash = cash_account[length(cash_account)],
      final_bonds = bond_value_daily[length(bond_value_daily)],
      tenor_constraints = c(min_tenor, max_tenor)
    )
  ))
}

# ============================================================================
# EXAMPLE USAGE
# ============================================================================

cat("\n" , rep("=", 80), "\n")
cat("EXECUTING TREASURY BONDS PORTFOLIO WITH DYNAMIC DURATION-BASED TENOR SELECTION\n")
cat("Treasury rates are zero rates, Duration = Maturity\n")
cat(rep("=", 80), "\n\n")

treasury_result <- construct_treasury_portfolio_duration(
  zero_tby_data = zero_tby,
  w0 = 1000000,
  alpha = 0.10,
  start_date = "2020-01-01",
  end_date = "2024-12-31",
  r_f_annual = 0.01,
  target_portfolio_duration = 10.0,
  min_target_duration = 9.0,
  max_target_duration = 11.0,
  min_price = 70,
  max_price = 130,
  max_daily_price_change = 0.10,
  face_value = 100,
  min_tenor = 5.0,
  max_tenor = 20.0
)

# Access results
cat("\n=== Results Available ===\n")
cat("treasury_result$portfolio - Portfolio values and returns over time\n")
cat("treasury_result$bond_positions - List of all bond purchases\n")
cat("treasury_result$daily_log - Detailed daily logs\n")
cat("treasury_result$purchase_info - Purchase information\n")
cat("treasury_result$duration_plot - Duration plot\n")
cat("treasury_result$portfolio_value_plot - Portfolio value plot\n")
cat("treasury_result$return_plot - Cumulative return plot\n")
cat("treasury_result$daily_return_plot - Daily return distribution\n")
cat("treasury_result$summary - Summary statistics\n")

# View portfolio head
cat("\n=== Portfolio Data (First 10 Rows) ===\n")
print(head(treasury_result$portfolio, 10))

# View purchase info
cat("\n=== Purchase Information ===\n")
print(treasury_result$purchase_info)

# Print summary
cat("\n=== Summary Statistics ===\n")
print(treasury_result$summary)

cat("\n" , rep("=", 80), "\n")
cat("TREASURY BONDS PORTFOLIO CONSTRUCTION COMPLETE\n")
cat(rep("=", 80), "\n\n")



```

# ============================================================================
# MULTI-PORTFOLIO COMPARISON WITH DURATION-BASED TENOR SELECTION
# ============================================================================

```{r}

# ============================================================================
# GLOBAL PARAMETERS FOR PORTFOLIO CONSTRUCTION
# ============================================================================

r_f_annual_param <- 0.01  # Annual risk-free rate 
w0 <- 1000000              # Initial wealth
alpha_param <- 0.10        # Alpha parameter

cat("\n=== Portfolio Construction Parameters ===\n")
cat("Initial Investment: $", format(w0, big.mark = ","), "\n")
cat("Risk-Free Rate (Annual): ", r_f_annual_param * 100, "%\n")
cat("Alpha: ", alpha_param, "\n\n")

# ============================================================================
# DEFINE MULTIPLE PURCHASE GROUPS
# ============================================================================

purchase_groups <- list(
  Group1 = California %>%
    filter(MUNI_TAX_PROV %in% c("FED TAXABLE/ST TAX-EXEMPT"), 
           CALLABLE == "FALSE"),
  
  Group2 = California %>%
    filter(S_AT_Iss == "Higher than 100",
           CALLABLE == "FALSE"),
  
  Group3 = California %>%
    filter(years_to_maturity_int == "Higher than 14.4",
           CALLABLE == "FALSE"),
  
  Group4 = California %>%
    filter(DAM == "Higher than 7",
           CALLABLE == "FALSE")
)

cat("\n=== Purchase Groups Defined ===\n")
for (group_name in names(purchase_groups)) {
  cat(group_name, ": ", nrow(purchase_groups[[group_name]]), " bonds\n", sep = "")
}
cat("\n")

# ============================================================================
# RUN PORTFOLIO CONSTRUCTION FOR ALL GREEN BOND GROUPS
# ============================================================================

cat("\n", rep("=", 80), "\n")
cat("RUNNING DURATION-BASED PORTFOLIO CONSTRUCTION FOR ALL GROUPS\n")
cat(rep("=", 80), "\n\n")

all_results <- list()

for (group_name in names(purchase_groups)) {
  
  cat("\n", rep("-", 80), "\n")
  cat("PROCESSING:", group_name, "\n")
  cat(rep("-", 80), "\n")
  cat("Number of bonds in purchase group:", nrow(purchase_groups[[group_name]]), "\n")
  
  # Show characteristics of this group
  cat("\nGroup Characteristics:\n")
  cat("  Median Coupon:", round(median(purchase_groups[[group_name]]$CPN, na.rm = TRUE), 2), "%\n")
  
  tax_summary <- purchase_groups[[group_name]] %>%
    group_by(MUNI_TAX_PROV) %>%
    summarise(n = n_distinct(ID_CUSIP), .groups = 'drop') %>%
    arrange(desc(n))
  
  cat("  Tax Provinces:\n")
  print(tax_summary)
  cat("  Most common:", tax_summary$MUNI_TAX_PROV[1], "\n")
  
  # Run portfolio construction with duration-based tenor selection
  result <- construct_portfolio_zcb_synthetic_duration(
    purchase_data = purchase_groups[[group_name]],
    par_data = par_data,
    w0 = w0,
    alpha = alpha_param,
    start_date = "2020-01-01",
    end_date = "2024-12-31",
    r_f_annual = r_f_annual_param,
    target_portfolio_duration = 10.0,
    min_target_duration = 9.0,
    max_target_duration = 11.0,
    min_price = 70,
    max_price = 130,
    max_daily_price_change = 0.03,
    coupon_frequency = 2,
    face_value = 100,
    duration_match_tolerance = 2.0,
    min_tenor = 5.0,
    max_tenor = 20.0
  )
  
  all_results[[group_name]] <- result
  
  cat("\n", rep("-", 80), "\n\n")
}

# ============================================================================
# RUN TREASURY PORTFOLIO CONSTRUCTION
# ============================================================================

cat("\n", rep("=", 80), "\n")
cat("RUNNING TREASURY PORTFOLIO CONSTRUCTION\n")
cat(rep("=", 80), "\n\n")

treasury_result <- construct_treasury_portfolio_duration(
  zero_tby_data = zero_tby,
  w0 = w0,
  alpha = alpha_param,
  start_date = "2020-01-01",
  end_date = "2024-12-31",
  r_f_annual = r_f_annual_param,
  target_portfolio_duration = 10.0,
  min_target_duration = 9.0,
  max_target_duration = 11.0,
  min_price = 20,
  max_price = 150,
  max_daily_price_change = 0.10,
  face_value = 100,
  min_tenor = 5.0,
  max_tenor = 20.0
)



```

# ============================================================================
# PORTFOLIO COMPARISON: ALL GROUPS + TREASURY (Fig 10)
# ============================================================================
```{r}
cat("\n", rep("=", 80), "\n")
cat("COMBINING ALL PORTFOLIOS FOR COMPARISON\n")
cat(rep("=", 80), "\n\n")

# Combine all portfolios including Treasury
comparison_df <- data.frame(Date = all_results[[1]]$portfolio$Date)

for (group_name in names(all_results)) {
  comparison_df[[group_name]] <- all_results[[group_name]]$portfolio$Portfolio_Value
}

# Add Treasury
comparison_df$Treasury <- treasury_result$portfolio$Portfolio_Value

# Add Year column for yearly analysis
comparison_df$Year <- year(comparison_df$Date)

# Convert to long format and calculate cumulative returns
plot_data <- comparison_df %>%
  pivot_longer(cols = -c(Date, Year),
               names_to = "Portfolio",
               values_to = "Portfolio_Value") %>%
  mutate(Cumulative_Return = (Portfolio_Value - w0) / w0 * 100)

# Create flexible color palette
n_portfolios <- length(unique(plot_data$Portfolio))
n_green_groups <- n_portfolios - 1

# Green shades for bond groups + navy for Treasury
color_palette <- c(
  colorRampPalette(c("darkgreen", "limegreen"))(n_green_groups),
  "navy"
)
names(color_palette) <- unique(plot_data$Portfolio)

cat("Portfolios included in comparison:\n")
print(unique(plot_data$Portfolio))
cat("\n")

# ============================================================================
# COMPARISON PLOTS (Framed, No Titles)
# ============================================================================

cat("=== Generating Comparison Plots ===\n\n")

# ---------------------------------------------------------------------------
# Plot 1: Portfolio Values
# ---------------------------------------------------------------------------
value_comparison_plot <- ggplot(plot_data, aes(x = Date, y = Portfolio_Value, color = Portfolio)) +
  geom_line(size = 1.2) +
  scale_y_continuous(labels = scales::dollar_format()) +
  scale_color_manual(values = color_palette) +
  labs(x = "Date",
       y = "Portfolio Value ($)",
       color = "Portfolio") +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    panel.border = element_rect(color = "black", fill = NA, linewidth = 0.8),
    panel.grid.minor = element_blank(),
    plot.title = element_blank(),
    plot.subtitle = element_blank()
  )

print(value_comparison_plot)

# ---------------------------------------------------------------------------
# Plot 2: Cumulative Returns
# ---------------------------------------------------------------------------
return_comparison_plot <- ggplot(plot_data, aes(x = Date, y = Cumulative_Return, color = Portfolio)) +
  geom_line(size = 1.2) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
  scale_color_manual(values = color_palette) +
  labs(x = "Date",
       y = "Cumulative Return (%)",
       color = "Portfolio") +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    panel.border = element_rect(color = "black", fill = NA, linewidth = 0.8),
    panel.grid.minor = element_blank(),
    plot.title = element_blank(),
    plot.subtitle = element_blank()
  )

print(return_comparison_plot)

# ---------------------------------------------------------------------------
# Plot 3: Duration Comparison
# ---------------------------------------------------------------------------
duration_data <- data.frame(Date = all_results[[1]]$portfolio$Date)

for (group_name in names(all_results)) {
  duration_data[[group_name]] <- all_results[[group_name]]$portfolio$Portfolio_Duration
}
duration_data$Treasury <- treasury_result$portfolio$Portfolio_Duration

duration_long <- duration_data %>%
  pivot_longer(cols = -Date,
               names_to = "Portfolio",
               values_to = "Duration")

duration_comparison_plot <- ggplot(duration_long %>% filter(!is.na(Duration)),
                                   aes(x = Date, y = Duration, color = Portfolio)) +
  geom_line(size = 1.2) +
  geom_hline(yintercept = 10, linetype = "dashed", color = "red", size = 1) +
  geom_ribbon(aes(ymin = 9, ymax = 11),
              alpha = 0.1, fill = "red", color = NA) +
  scale_color_manual(values = color_palette) +
  labs(x = "Date",
       y = "Duration (Years)",
       color = "Portfolio") +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    panel.border = element_rect(color = "black", fill = NA, linewidth = 0.8),
    panel.grid.minor = element_blank(),
    plot.title = element_blank(),
    plot.subtitle = element_blank()
  )

print(duration_comparison_plot)
```

# ============================================================================
# HELPER FUNCTIONS FOR PERFORMANCE METRICS
# ============================================================================
```{r}


# Function to calculate daily returns
calc_daily_returns <- function(values) {
  returns <- diff(values) / head(values, -1)
  return(returns)
}

# Function to calculate maximum drawdown
calc_max_drawdown <- function(values) {
  cummax_values <- cummax(values)
  drawdowns <- (values - cummax_values) / cummax_values
  max_drawdown <- min(drawdowns, na.rm = TRUE) * 100  # as percentage
  return(max_drawdown)
}

# Function to calculate all performance metrics for a given period
calc_performance_metrics <- function(values, dates, r_f_annual) {
  
  # Risk-free rate (daily)
  rf_rate_daily <- (1 + r_f_annual)^(1/252) - 1
  
  # Calculate returns
  initial_value <- values[1]
  final_value <- tail(values, 1)
  total_return_pct <- (final_value - initial_value) / initial_value * 100
  
  # Daily returns
  daily_returns <- calc_daily_returns(values)
  
  # Excess returns
  excess_returns <- daily_returns - rf_rate_daily
  
  # Sharpe Ratio
  mean_excess <- mean(excess_returns, na.rm = TRUE)
  sd_returns <- sd(daily_returns, na.rm = TRUE)
  sharpe_ratio <- mean_excess / sd_returns * sqrt(252)
  
  # Sortino Ratio (only downside deviation)
  downside_returns <- excess_returns[excess_returns < 0]
  if (length(downside_returns) > 0) {
    downside_deviation <- sd(downside_returns, na.rm = TRUE)
    sortino_ratio <- mean_excess / downside_deviation * sqrt(252)
  } else {
    sortino_ratio <- NA
  }
  
  # Maximum Drawdown
  max_dd <- calc_max_drawdown(values)
  
  # Annualized Volatility
  ann_vol <- sd_returns * sqrt(252) * 100
  
  return(list(
    Initial_Value = initial_value,
    Final_Value = final_value,
    Total_Return_Pct = total_return_pct,
    Sharpe_Ratio = sharpe_ratio,
    Sortino_Ratio = sortino_ratio,
    Max_Drawdown_Pct = max_dd,
    Ann_Volatility = ann_vol
  ))
}
```


# ============================================================================
# OVERALL PERFORMANCE METRICS
# ============================================================================
```{r}
cat("\n", rep("=", 80), "\n")
cat("CALCULATING OVERALL PERFORMANCE METRICS (2020-2024)\n")
cat(rep("=", 80), "\n\n")

all_portfolios <- c(names(all_results), "Treasury")

performance_metrics_overall <- data.frame(
  Portfolio = character(),
  Initial_Value = numeric(),
  Final_Value = numeric(),
  Total_Return_Pct = numeric(),
  Sharpe_Ratio = numeric(),
  Sortino_Ratio = numeric(),
  Max_Drawdown_Pct = numeric(),
  Ann_Volatility = numeric(),
  stringsAsFactors = FALSE
)

for (portfolio_name in all_portfolios) {
  
  # Get portfolio values
  if (portfolio_name == "Treasury") {
    values <- treasury_result$portfolio$Portfolio_Value
    dates <- treasury_result$portfolio$Date
  } else {
    values <- all_results[[portfolio_name]]$portfolio$Portfolio_Value
    dates <- all_results[[portfolio_name]]$portfolio$Date
  }
  
  # Calculate metrics
  metrics <- calc_performance_metrics(values, dates, r_f_annual_param)
  
  # Add to dataframe
  performance_metrics_overall <- rbind(performance_metrics_overall, 
                                       data.frame(
                                         Portfolio = portfolio_name,
                                         Initial_Value = metrics$Initial_Value,
                                         Final_Value = metrics$Final_Value,
                                         Total_Return_Pct = metrics$Total_Return_Pct,
                                         Sharpe_Ratio = metrics$Sharpe_Ratio,
                                         Sortino_Ratio = metrics$Sortino_Ratio,
                                         Max_Drawdown_Pct = metrics$Max_Drawdown_Pct,
                                         Ann_Volatility = metrics$Ann_Volatility
                                       ))
}

cat("=== Overall Performance Metrics ===\n\n")
print(performance_metrics_overall)
cat("\n")

```

# ============================================================================
# YEARLY PERFORMANCE METRICS
# ============================================================================
```{r}
cat("\n", rep("=", 80), "\n")
cat("CALCULATING YEARLY PERFORMANCE METRICS\n")
cat(rep("=", 80), "\n\n")

years <- sort(unique(comparison_df$Year))
performance_metrics_yearly <- list()

for (yr in years) {
  
  yearly_metrics <- data.frame(
    Portfolio = character(),
    Year = integer(),
    Initial_Value = numeric(),
    Final_Value = numeric(),
    Total_Return_Pct = numeric(),
    Sharpe_Ratio = numeric(),
    Sortino_Ratio = numeric(),
    Max_Drawdown_Pct = numeric(),
    stringsAsFactors = FALSE
  )
  
  for (portfolio_name in all_portfolios) {
    
    # Get portfolio values for this year
    if (portfolio_name == "Treasury") {
      year_data <- treasury_result$portfolio %>%
        filter(year(Date) == yr)
      values <- year_data$Portfolio_Value
      dates <- year_data$Date
    } else {
      year_data <- all_results[[portfolio_name]]$portfolio %>%
        filter(year(Date) == yr)
      values <- year_data$Portfolio_Value
      dates <- year_data$Date
    }
    
    # Skip if no data for this year
    if (length(values) == 0) next
    
    # Calculate metrics
    metrics <- calc_performance_metrics(values, dates, r_f_annual_param)
    
    # Add to dataframe
    yearly_metrics <- rbind(yearly_metrics, 
                            data.frame(
                              Portfolio = portfolio_name,
                              Year = yr,
                              Initial_Value = metrics$Initial_Value,
                              Final_Value = metrics$Final_Value,
                              Total_Return_Pct = metrics$Total_Return_Pct,
                              Sharpe_Ratio = metrics$Sharpe_Ratio,
                              Sortino_Ratio = metrics$Sortino_Ratio,
                              Max_Drawdown_Pct = metrics$Max_Drawdown_Pct
                            ))
  }
  
  performance_metrics_yearly[[as.character(yr)]] <- yearly_metrics
  
  cat("=== Year", yr, "===\n")
  print(yearly_metrics)
  cat("\n")
}

# ============================================================================
# PLOT 4: DAILY RETURNS DISTRIBUTION COMPARISON (SEPARATE PANELS)
# ============================================================================

cat("=== Generating Returns Distribution Plot (Separate Panels) ===\n\n")

returns_data <- data.frame()

for (portfolio_name in all_portfolios) {
  
  # Get portfolio values
  if (portfolio_name == "Treasury") {
    portfolio_df <- treasury_result$portfolio %>%
      mutate(Year = year(Date))
  } else {
    portfolio_df <- all_results[[portfolio_name]]$portfolio %>%
      mutate(Year = year(Date))
  }
  
  # Calculate daily returns
  daily_returns <- calc_daily_returns(portfolio_df$Portfolio_Value) * 100  # as percentage
  
  returns_df <- data.frame(
    Portfolio = portfolio_name,
    Daily_Return = daily_returns
  )
  
  returns_data <- rbind(returns_data, returns_df)
}

returns_dist_plot <- ggplot(returns_data %>% filter(!is.na(Daily_Return)), 
                           aes(x = Daily_Return, fill = Portfolio)) +
  geom_density(alpha = 0.6) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "black", size = 0.5) +
  scale_fill_manual(values = color_palette) +
  facet_wrap(~ Portfolio, nrow = 1, scales = "free_y") +
  labs(title = "Overall Daily Returns Distribution Comparison (2020-2024)",
       subtitle = "Separate panels for each portfolio",
       x = "Daily Return (%)",
       y = "Density") +
  theme_minimal() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", size = 14),
        strip.text = element_text(face = "bold"))

print(returns_dist_plot)

# ============================================================================
# PLOT 6: YEARLY DENSITY CHARTS FOR RETURNS (GRID LAYOUT)
# ============================================================================

cat("\n=== Generating Yearly Density Charts (Grid Layout) ===\n\n")

# Collect all yearly returns data
all_yearly_returns_data <- data.frame()

for (yr in years) {
  
  for (portfolio_name in all_portfolios) {
    
    # Get portfolio values for this year
    if (portfolio_name == "Treasury") {
      year_portfolio <- treasury_result$portfolio %>%
        filter(year(Date) == yr)
    } else {
      year_portfolio <- all_results[[portfolio_name]]$portfolio %>%
        filter(year(Date) == yr)
    }
    
    # Calculate daily returns for this year
    if (nrow(year_portfolio) > 1) {
      year_daily_returns <- calc_daily_returns(year_portfolio$Portfolio_Value) * 100  # as percentage
      
      year_returns_df <- data.frame(
        Portfolio = portfolio_name,
        Daily_Return = year_daily_returns,
        Year = yr
      )
      
      all_yearly_returns_data <- rbind(all_yearly_returns_data, year_returns_df)
    }
  }
}

# Create grid plot with years as columns and portfolios as rows
yearly_density_grid_plot <- ggplot(all_yearly_returns_data %>% filter(!is.na(Daily_Return)), 
                                    aes(x = Daily_Return, fill = Portfolio)) +
  geom_density(alpha = 0.6) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "black", size = 0.5) +
  scale_fill_manual(values = color_palette) +
  facet_grid(Portfolio ~ Year, scales = "free_y") +
  labs(title = "Daily Returns Distribution by Year and Portfolio",
       subtitle = "Grid Layout: Rows = Portfolios, Columns = Years",
       x = "Daily Return (%)",
       y = "Density") +
  theme_minimal() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", size = 14),
        strip.text = element_text(face = "bold"))

print(yearly_density_grid_plot)

cat("\n")


```


# ============================================================================
# box plots - all duration-based portfolios (Groups) + treasury (Fig 11)
# ============================================================================

```{r}
# Prepare data for box plots - all duration-based portfolios + treasury
box_data_all <- data.frame()

# Get list of duration-based portfolio groups
duration_portfolios <- names(all_results)

# Add all duration-based portfolios
for (i in seq_along(duration_portfolios)) {
  group_port <- duration_portfolios[i]
  
  portfolio_data <- all_results[[group_port]]$portfolio %>%
    mutate(Year = year(Date))
  
  # Yearly data
  for (yr in years) {
    year_data <- portfolio_data %>% filter(Year == yr)
    if (nrow(year_data) > 1) {
      daily_returns <- calc_daily_returns(year_data$Portfolio_Value)
      box_data_all <- rbind(box_data_all, data.frame(
        Portfolio = group_port,
        Year = as.character(yr),
        Daily_Return = daily_returns,
        Portfolio_Order = i
      ))
    }
  }
  
  # Overall data
  daily_returns_overall <- calc_daily_returns(portfolio_data$Portfolio_Value)
  box_data_all <- rbind(box_data_all, data.frame(
    Portfolio = group_port,
    Year = "Overall",
    Daily_Return = daily_returns_overall,
    Portfolio_Order = i
  ))
}

# Add Treasury
treasury_data_year <- treasury_result$portfolio %>%
  mutate(Year = year(Date))

for (yr in years) {
  year_data <- treasury_data_year %>% filter(Year == yr)
  if (nrow(year_data) > 1) {
    daily_returns <- calc_daily_returns(year_data$Portfolio_Value)
    box_data_all <- rbind(box_data_all, data.frame(
      Portfolio = "Treasury",
      Year = as.character(yr),
      Daily_Return = daily_returns,
      Portfolio_Order = length(duration_portfolios) + 1
    ))
  }
}

# Overall Treasury
daily_returns_treasury_overall <- calc_daily_returns(treasury_result$portfolio$Portfolio_Value)
box_data_all <- rbind(box_data_all, data.frame(
  Portfolio = "Treasury",
  Year = "Overall",
  Daily_Return = daily_returns_treasury_overall,
  Portfolio_Order = length(duration_portfolios) + 1
))

# Create color palette
n_duration_groups <- length(duration_portfolios)
color_palette <- c(
  colorRampPalette(c("darkgreen", "limegreen"))(n_duration_groups),
  "navy"
)

# Set portfolio factor levels for consistent ordering
portfolio_levels <- c(duration_portfolios, "Treasury")
box_data_all$Portfolio <- factor(box_data_all$Portfolio, levels = portfolio_levels)

# Set Year factor levels to control facet order
year_levels <- c(as.character(years), "Overall")
box_data_all$Year <- factor(box_data_all$Year, levels = year_levels)

# Calculate consistent y-axis limits
y_range <- range(box_data_all$Daily_Return, na.rm = TRUE)
y_padding <- diff(y_range) * 0.05
y_limits <- c(y_range[1] - y_padding, y_range[2] + y_padding)

# Create combined plot with facets
p_combined <- ggplot(box_data_all, aes(x = Portfolio, y = Daily_Return, fill = Portfolio)) +
  geom_boxplot(outlier.size = 0.5, outlier.alpha = 0.3, width = 0.6) +
  facet_wrap(~ Year, nrow = 1) +
  scale_fill_manual(values = color_palette) +
  coord_cartesian(ylim = y_limits) +
  labs(
    #title = "Daily Return Distribution (Yearly + Overall): Duration-Based Portfolios vs Treasury",
    x = "Portfolio",
    y = "Daily Return (%)"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold", size = 14, hjust = 0.5),
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1, size = 8),
    axis.title = element_text(size = 11, face = "bold"),
    strip.text = element_text(face = "bold", size = 10),
    # Frame around entire plot
    plot.background = element_rect(color = "black", fill = NA, linewidth = 1),
    # Frame around each panel
    panel.border = element_rect(color = "black", fill = NA, linewidth = 0.6),
    panel.grid.major = element_line(color = "grey90"),
    panel.grid.minor = element_blank(),
    panel.spacing = unit(0.5, "lines")
  )

print(p_combined)

```


# ============================================================================
# RISK-RETURN SCATTER PLOTS - DURATION-BASED PORTFOLIOS (Fig 12)
# ============================================================================
```{r}


# Prepare scatter data for all years + overall
scatter_data_all_years <- data.frame()

# Get list of duration-based portfolio groups
duration_portfolios <- names(all_results)

# Color palette
n_duration_groups <- length(duration_portfolios)
color_palette <- c(
  colorRampPalette(c("darkgreen", "limegreen"))(n_duration_groups),
  "navy"
)
names(color_palette) <- c(duration_portfolios, "Treasury")

# Risk-free rate (daily) - using 1% annual
rf_rate_daily <- (1 + 0.01)^(1/252) - 1

# Calculate metrics for each year
for (yr in years) {
  
  # Duration-based portfolios
  for (i in seq_along(duration_portfolios)) {
    group_port <- duration_portfolios[i]
    
    portfolio_data <- all_results[[group_port]]$portfolio %>%
      filter(year(Date) == yr)
    
    if (nrow(portfolio_data) > 1) {
      daily_returns <- calc_daily_returns(portfolio_data$Portfolio_Value)
      total_return <- (tail(portfolio_data$Portfolio_Value, 1) / 
                      head(portfolio_data$Portfolio_Value, 1) - 1) * 100
      volatility <- sd(daily_returns, na.rm = TRUE) * sqrt(252) * 100
      
      # Calculate Sharpe ratio
      excess_returns <- daily_returns - rf_rate_daily
      mean_excess <- mean(excess_returns, na.rm = TRUE)
      sd_returns <- sd(daily_returns, na.rm = TRUE)
      sharpe <- mean_excess / sd_returns * sqrt(252)
      
      scatter_data_all_years <- rbind(scatter_data_all_years, data.frame(
        Portfolio = group_port,
        Year = as.character(yr),
        Return = total_return,
        Volatility = volatility,
        Sharpe = sharpe,
        Portfolio_Order = i
      ))
    }
  }
  
  # Treasury
  treasury_data <- treasury_result$portfolio %>%
    filter(year(Date) == yr)
  
  if (nrow(treasury_data) > 1) {
    daily_returns <- calc_daily_returns(treasury_data$Portfolio_Value)
    total_return <- (tail(treasury_data$Portfolio_Value, 1) / 
                    head(treasury_data$Portfolio_Value, 1) - 1) * 100
    volatility <- sd(daily_returns, na.rm = TRUE) * sqrt(252) * 100
    
    # Calculate Sharpe ratio
    excess_returns <- daily_returns - rf_rate_daily
    mean_excess <- mean(excess_returns, na.rm = TRUE)
    sd_returns <- sd(daily_returns, na.rm = TRUE)
    sharpe <- mean_excess / sd_returns * sqrt(252)
    
    scatter_data_all_years <- rbind(scatter_data_all_years, data.frame(
      Portfolio = "Treasury",
      Year = as.character(yr),
      Return = total_return,
      Volatility = volatility,
      Sharpe = sharpe,
      Portfolio_Order = length(duration_portfolios) + 1
    ))
  }
}

# Calculate metrics for overall period
for (i in seq_along(duration_portfolios)) {
  group_port <- duration_portfolios[i]
  
  portfolio_data <- all_results[[group_port]]$portfolio
  daily_returns <- calc_daily_returns(portfolio_data$Portfolio_Value)
  total_return <- (tail(portfolio_data$Portfolio_Value, 1) / 
                  head(portfolio_data$Portfolio_Value, 1) - 1) * 100
  volatility <- sd(daily_returns, na.rm = TRUE) * sqrt(252) * 100
  
  # Calculate Sharpe ratio
  excess_returns <- daily_returns - rf_rate_daily
  mean_excess <- mean(excess_returns, na.rm = TRUE)
  sd_returns <- sd(daily_returns, na.rm = TRUE)
  sharpe <- mean_excess / sd_returns * sqrt(252)
  
  scatter_data_all_years <- rbind(scatter_data_all_years, data.frame(
    Portfolio = group_port,
    Year = "Overall",
    Return = total_return,
    Volatility = volatility,
    Sharpe = sharpe,
    Portfolio_Order = i
  ))
}

# Overall Treasury
daily_returns <- calc_daily_returns(treasury_result$portfolio$Portfolio_Value)
total_return <- (tail(treasury_result$portfolio$Portfolio_Value, 1) / 
                head(treasury_result$portfolio$Portfolio_Value, 1) - 1) * 100
volatility <- sd(daily_returns, na.rm = TRUE) * sqrt(252) * 100

# Calculate Sharpe ratio
excess_returns <- daily_returns - rf_rate_daily
mean_excess <- mean(excess_returns, na.rm = TRUE)
sd_returns <- sd(daily_returns, na.rm = TRUE)
sharpe <- mean_excess / sd_returns * sqrt(252)

scatter_data_all_years <- rbind(scatter_data_all_years, data.frame(
  Portfolio = "Treasury",
  Year = "Overall",
  Return = total_return,
  Volatility = volatility,
  Sharpe = sharpe,
  Portfolio_Order = length(duration_portfolios) + 1
))

# Calculate consistent axis limits
vol_range <- range(scatter_data_all_years$Volatility, na.rm = TRUE)
ret_range <- range(scatter_data_all_years$Return, na.rm = TRUE)
vol_padding <- diff(vol_range) * 0.1
ret_padding <- diff(ret_range) * 0.1
vol_limits <- c(vol_range[1] - vol_padding, vol_range[2] + vol_padding)
ret_limits <- c(ret_range[1] - ret_padding, ret_range[2] + ret_padding)

cat("\n=== Consistent axis limits ===")
cat("\nVolatility:", round(vol_limits[1], 2), "to", round(vol_limits[2], 2))
cat("\nReturn:", round(ret_limits[1], 2), "to", round(ret_limits[2], 2), "\n\n")

# Create plots for each year
for (yr in years) {
  
  cat("--- Risk-return scatter for year:", yr, "---\n")
  
  yearly_data <- scatter_data_all_years %>% 
    filter(Year == as.character(yr)) %>%
    mutate(Portfolio = factor(Portfolio, levels = c(duration_portfolios, "Treasury")))
  
  p_year <- ggplot(yearly_data, aes(x = Volatility, y = Return, 
                                     color = Portfolio, size = Sharpe)) +
    geom_point(alpha = 0.8) +
    geom_label_repel(
      aes(label = Portfolio), 
      size = 3.5,
      box.padding = 0.8,
      point.padding = 0.5,
      segment.color = "grey50",
      segment.size = 0.3,
      max.overlaps = 20,
      show.legend = FALSE,
      force = 2,
      min.segment.length = 0,
      fill = alpha("white", 0.9),
      label.padding = unit(0.25, "lines")
    ) +
    scale_color_manual(
      values = color_palette,
      name = "Portfolio"
    ) +
    scale_size_continuous(
      range = c(3, 12), 
      name = "Sharpe Ratio"
    ) +
    coord_cartesian(xlim = vol_limits, ylim = ret_limits) +
    labs(
      #title = paste( yr),
      #subtitle = "Point size represents Sharpe ratio | Duration-Based Portfolios",
      x = "Volatility (Annualized %)",
      y = "Total Return (%)"
    ) +
    guides(
      color = guide_legend(
        title.position = "top",
        title.hjust = 0.5,
        nrow = 2,
        override.aes = list(size = 4, alpha = 0.9)
      ),
      size = guide_legend(
        title.position = "top",
        title.hjust = 0.5,
        nrow = 3,
        override.aes = list(alpha = 0.8)
      )
    ) +
    theme_minimal() +
    theme(
      plot.title = element_text(face = "bold", size = 14, hjust = 0.5),
      plot.subtitle = element_text(size = 11, hjust = 0.5),
      legend.position = "right",
      legend.box = "vertical",
      legend.spacing = unit(0.2, "cm"),
      legend.title = element_text(size = 9, face = "bold"),
      legend.text = element_text(size = 8),
      legend.key.size = unit(0.3, "cm"),
      legend.key.height = unit(0.3, "cm"),
      legend.key.width = unit(0.3, "cm"),
      legend.margin = margin(t = 0, r = 3, b = 0, l = 3),
      legend.box.spacing = unit(0.1, "cm"),
      panel.border = element_rect(color = "black", fill = NA, linewidth = 0.8),
      panel.grid.major = element_line(color = "grey90"),
      panel.grid.minor = element_blank()
    )
  
  print(p_year)
}

# Create plot for overall period
cat("--- Risk-return scatter for Overall period ---\n")

overall_data <- scatter_data_all_years %>% 
  filter(Year == "Overall") %>%
  mutate(Portfolio = factor(Portfolio, levels = c(duration_portfolios, "Treasury")))

p_overall <- ggplot(overall_data, aes(x = Volatility, y = Return, 
                                       color = Portfolio, size = Sharpe)) +
  geom_point(alpha = 0.8) +
  geom_label_repel(
    aes(label = Portfolio), 
    size = 3.5,
    box.padding = 0.8,
    point.padding = 0.5,
    segment.color = "grey50",
    segment.size = 0.3,
    max.overlaps = 20,
    show.legend = FALSE,
    force = 2,
    min.segment.length = 0,
    fill = alpha("white", 0.9),
    label.padding = unit(0.25, "lines")
  ) +
  scale_color_manual(
    values = color_palette,
    name = "Portfolio"
  ) +
  scale_size_continuous(
    range = c(3, 12), 
    name = "Sharpe Ratio"
  ) +
  coord_cartesian(xlim = vol_limits, ylim = ret_limits) +
  labs(
    #title = "Risk-Return Profile: Overall Period (2020-2024)",
    #subtitle = "Point size represents Sharpe ratio | Duration-Based Portfolios",
    x = "Volatility (Annualized %)",
    y = "Total Return (%)"
  ) +
  guides(
    color = guide_legend(
      title.position = "top",
      title.hjust = 0.5,
      nrow = 2,
      override.aes = list(size = 4, alpha = 0.9)
    ),
    size = guide_legend(
      title.position = "top",
      title.hjust = 0.5,
      nrow = 3,
      override.aes = list(alpha = 0.8)
    )
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold", size = 14, hjust = 0.5),
    plot.subtitle = element_text(size = 11, hjust = 0.5),
    legend.position = "right",
    legend.box = "vertical",
    legend.spacing = unit(0.2, "cm"),
    legend.title = element_text(size = 9, face = "bold"),
    legend.text = element_text(size = 8),
    legend.key.size = unit(0.3, "cm"),
    legend.key.height = unit(0.3, "cm"),
    legend.key.width = unit(0.3, "cm"),
    legend.margin = margin(t = 0, r = 3, b = 0, l = 3),
    legend.box.spacing = unit(0.1, "cm"),
    panel.border = element_rect(color = "black", fill = NA, linewidth = 0.8),
    panel.grid.major = element_line(color = "grey90"),
    panel.grid.minor = element_blank()
  )

print(p_overall)
```

# ============================================================================
# DETAILED COMPARISON TABLES BY YEAR
# ============================================================================
```{r}
cat("\n", rep("=", 80), "\n")
cat("DETAILED PERFORMANCE COMPARISON TABLES BY YEAR\n")
cat(rep("=", 80), "\n\n")

for (yr in years) {
  
  cat("\n=== YEAR ", yr, " - DETAILED COMPARISON ===\n\n", sep = "")
  
  yearly_data <- performance_metrics_yearly[[as.character(yr)]]
  
  if (!is.null(yearly_data) && nrow(yearly_data) > 0) {
    
    # Create comparison table
    comparison_table_year <- yearly_data %>%
      dpylr::select(Portfolio, Initial_Value, Final_Value, Total_Return_Pct, 
             Sharpe_Ratio, Sortino_Ratio, Max_Drawdown_Pct) %>%
      arrange(desc(Total_Return_Pct))
    
    # Round values for display (3 decimal places)
    comparison_table_year$Initial_Value <- round(comparison_table_year$Initial_Value, 3)
    comparison_table_year$Final_Value <- round(comparison_table_year$Final_Value, 3)
    comparison_table_year$Total_Return_Pct <- round(comparison_table_year$Total_Return_Pct, 3)
    comparison_table_year$Sharpe_Ratio <- round(comparison_table_year$Sharpe_Ratio, 3)
    comparison_table_year$Sortino_Ratio <- round(comparison_table_year$Sortino_Ratio, 3)
    comparison_table_year$Max_Drawdown_Pct <- round(comparison_table_year$Max_Drawdown_Pct, 3)
    
    print(comparison_table_year)
    
    # Calculate statistics
    cat("\n--- Year ", yr, " Summary Statistics ---\n", sep = "")
    cat("Best Return: ", comparison_table_year$Portfolio[1], " (", 
        comparison_table_year$Total_Return_Pct[1], "%)\n", sep = "")
    
    best_sharpe_idx <- which.max(comparison_table_year$Sharpe_Ratio)
    cat("Best Sharpe: ", comparison_table_year$Portfolio[best_sharpe_idx], " (", 
        comparison_table_year$Sharpe_Ratio[best_sharpe_idx], ")\n", sep = "")
    
    best_dd_idx <- which.max(comparison_table_year$Max_Drawdown_Pct)
    cat("Lowest Drawdown: ", comparison_table_year$Portfolio[best_dd_idx], " (", 
        comparison_table_year$Max_Drawdown_Pct[best_dd_idx], "%)\n", sep = "")
    
    cat("\n")
  }
}

# ============================================================================
# OVERALL COMPARISON TABLE (FORMATTED)
# ============================================================================

cat("\n", rep("=", 80), "\n")
cat("OVERALL PERFORMANCE COMPARISON TABLE (2020-2024)\n")
cat(rep("=", 80), "\n\n")

comparison_table_overall <- performance_metrics_overall %>%
  arrange(desc(Total_Return_Pct))

# Round for display (3 decimals)
comparison_table_overall_display <- comparison_table_overall
comparison_table_overall_display$Initial_Value <- round(comparison_table_overall_display$Initial_Value, 3)
comparison_table_overall_display$Final_Value <- round(comparison_table_overall_display$Final_Value, 3)
comparison_table_overall_display$Total_Return_Pct <- round(comparison_table_overall_display$Total_Return_Pct, 3)
comparison_table_overall_display$Sharpe_Ratio <- round(comparison_table_overall_display$Sharpe_Ratio, 3)
comparison_table_overall_display$Sortino_Ratio <- round(comparison_table_overall_display$Sortino_Ratio, 3)
comparison_table_overall_display$Max_Drawdown_Pct <- round(comparison_table_overall_display$Max_Drawdown_Pct, 3)
comparison_table_overall_display$Ann_Volatility <- round(comparison_table_overall_display$Ann_Volatility, 3)

print(comparison_table_overall_display)

cat("\n")

# ============================================================================
# LATEX TABLE GENERATION (3 DECIMALS)
# ============================================================================

cat("\n", rep("=", 80), "\n")
cat("GENERATING LATEX TABLE FOR OVERLEAF\n")
cat(rep("=", 80), "\n\n")

# Create LaTeX table structure
latex_table <- data.frame(Portfolio = all_portfolios)

# Add columns for each year - Returns
for (yr in years) {
  yearly_data <- performance_metrics_yearly[[as.character(yr)]]
  col_name <- paste0("Return_", yr)
  latex_table[[col_name]] <- sapply(all_portfolios, function(p) {
    idx <- which(yearly_data$Portfolio == p)
    if (length(idx) > 0) yearly_data$Total_Return_Pct[idx] else NA
  })
}

# Add columns for each year - Sharpe
for (yr in years) {
  yearly_data <- performance_metrics_yearly[[as.character(yr)]]
  col_name <- paste0("Sharpe_", yr)
  latex_table[[col_name]] <- sapply(all_portfolios, function(p) {
    idx <- which(yearly_data$Portfolio == p)
    if (length(idx) > 0) yearly_data$Sharpe_Ratio[idx] else NA
  })
}

# Add columns for each year - Sortino
for (yr in years) {
  yearly_data <- performance_metrics_yearly[[as.character(yr)]]
  col_name <- paste0("Sortino_", yr)
  latex_table[[col_name]] <- sapply(all_portfolios, function(p) {
    idx <- which(yearly_data$Portfolio == p)
    if (length(idx) > 0) yearly_data$Sortino_Ratio[idx] else NA
  })
}

# Add columns for each year - Max Drawdown
for (yr in years) {
  yearly_data <- performance_metrics_yearly[[as.character(yr)]]
  col_name <- paste0("MaxDD_", yr)
  latex_table[[col_name]] <- sapply(all_portfolios, function(p) {
    idx <- which(yearly_data$Portfolio == p)
    if (length(idx) > 0) yearly_data$Max_Drawdown_Pct[idx] else NA
  })
}

# Add overall columns
latex_table$Return_Overall <- sapply(all_portfolios, function(p) {
  idx <- which(performance_metrics_overall$Portfolio == p)
  performance_metrics_overall$Total_Return_Pct[idx]
})

latex_table$Sharpe_Overall <- sapply(all_portfolios, function(p) {
  idx <- which(performance_metrics_overall$Portfolio == p)
  performance_metrics_overall$Sharpe_Ratio[idx]
})

latex_table$Sortino_Overall <- sapply(all_portfolios, function(p) {
  idx <- which(performance_metrics_overall$Portfolio == p)
  performance_metrics_overall$Sortino_Ratio[idx]
})

latex_table$MaxDD_Overall <- sapply(all_portfolios, function(p) {
  idx <- which(performance_metrics_overall$Portfolio == p)
  performance_metrics_overall$Max_Drawdown_Pct[idx]
})

# Generate LaTeX table with 3 decimal places
cat("\\begin{table}[htbp]\n")
cat("\\centering\n")
cat("\\caption{Portfolio Performance Metrics by Year and Overall (2020--2024)}\n")
cat("\\label{tab:performance_duration_based}\n")
cat("\\resizebox{\\textwidth}{!}{\n")
cat("\\begin{tabular}{l", paste(rep("r", ncol(latex_table) - 1), collapse = ""), "}\n")
cat("\\hline\\hline\n")

# Header rows
header1 <- "Portfolio"
for (yr in years) {
  header1 <- paste0(header1, " & \\multicolumn{4}{c}{", yr, "}")
}
header1 <- paste0(header1, " & \\multicolumn{4}{c}{Overall} \\\\\n")
cat(header1)

header2 <- " "
for (yr in c(years, "Overall")) {
  header2 <- paste0(header2, " & Return & Sharpe & Sortino & Max DD")
}
header2 <- paste0(header2, " \\\\\n")
cat(header2)

header3 <- " "
for (yr in c(years, "Overall")) {
  header3 <- paste0(header3, " & (\\%) & & & (\\%)")
}
header3 <- paste0(header3, " \\\\\n")
cat(header3)

cat("\\hline\n")

# Data rows (3 decimals)
for (i in 1:nrow(latex_table)) {
  row_str <- latex_table$Portfolio[i]
  
  for (yr in years) {
    ret <- sprintf("%.3f", latex_table[[paste0("Return_", yr)]][i])
    sha <- sprintf("%.3f", latex_table[[paste0("Sharpe_", yr)]][i])
    sor <- sprintf("%.3f", latex_table[[paste0("Sortino_", yr)]][i])
    mdd <- sprintf("%.3f", latex_table[[paste0("MaxDD_", yr)]][i])
    row_str <- paste0(row_str, " & ", ret, " & ", sha, " & ", sor, " & ", mdd)
  }
  
  # Overall
  ret_ov <- sprintf("%.3f", latex_table$Return_Overall[i])
  sha_ov <- sprintf("%.3f", latex_table$Sharpe_Overall[i])
  sor_ov <- sprintf("%.3f", latex_table$Sortino_Overall[i])
  mdd_ov <- sprintf("%.3f", latex_table$MaxDD_Overall[i])
  row_str <- paste0(row_str, " & ", ret_ov, " & ", sha_ov, " & ", sor_ov, " & ", mdd_ov)
  
  cat(row_str, " \\\\\n")
}

cat("\\hline\\hline\n")
cat("\\end{tabular}\n")
cat("}\n")
cat("\\end{table}\n\n")

# ============================================================================
# SUMMARY STATISTICS
# ============================================================================

cat("\n", rep("=", 80), "\n")
cat("SUMMARY: BEST PERFORMING PORTFOLIOS\n")
cat(rep("=", 80), "\n\n")

# Best by Total Return
best_return_idx <- which.max(performance_metrics_overall$Total_Return_Pct)
cat("Highest Total Return:\n")
cat("  Portfolio:", performance_metrics_overall$Portfolio[best_return_idx], "\n")
cat("  Return:", round(performance_metrics_overall$Total_Return_Pct[best_return_idx], 3), "%\n\n")

# Best by Sharpe Ratio
best_sharpe_idx <- which.max(performance_metrics_overall$Sharpe_Ratio)
cat("Highest Sharpe Ratio:\n")
cat("  Portfolio:", performance_metrics_overall$Portfolio[best_sharpe_idx], "\n")
cat("  Sharpe:", round(performance_metrics_overall$Sharpe_Ratio[best_sharpe_idx], 3), "\n\n")

# Lowest Max Drawdown (least negative)
best_dd_idx <- which.max(performance_metrics_overall$Max_Drawdown_Pct)
cat("Lowest Max Drawdown:\n")
cat("  Portfolio:", performance_metrics_overall$Portfolio[best_dd_idx], "\n")
cat("  Max DD:", round(performance_metrics_overall$Max_Drawdown_Pct[best_dd_idx], 3), "%\n\n")

# Lowest Volatility
best_vol_idx <- which.min(performance_metrics_overall$Ann_Volatility)
cat("Lowest Volatility:\n")
cat("  Portfolio:", performance_metrics_overall$Portfolio[best_vol_idx], "\n")
cat("  Ann. Vol:", round(performance_metrics_overall$Ann_Volatility[best_vol_idx], 3), "%\n\n")

cat(rep("=", 80), "\n")
cat("MULTI-PORTFOLIO COMPARISON COMPLETE\n")
cat(rep("=", 80), "\n\n")

# ============================================================================
# STORE RESULTS
# ============================================================================

comparison_results <- list(
  performance_overall = performance_metrics_overall,
  performance_yearly = performance_metrics_yearly,
  comparison_table_overall = comparison_table_overall_display,
  latex_table = latex_table,
  all_portfolio_results = all_results,
  treasury_result = treasury_result
)

cat("=== Results Stored ===\n")
cat("comparison_results$performance_overall - Overall metrics table\n")
cat("comparison_results$performance_yearly - Yearly metrics by portfolio\n")
cat("comparison_results$latex_table - LaTeX table for publication\n")
cat("comparison_results$all_portfolio_results - Individual portfolio results\n")
cat("comparison_results$treasury_result - Treasury portfolio result\n")





```


# ============================================================================
# HYBRID PORTFOLIOS: CONVEX COMBINATIONS OF GREEN + TREASURY
# ============================================================================
```{r}
cat("\n\n", rep("=", 100), "\n")
cat("HYBRID PORTFOLIO CONSTRUCTION\n")
cat(rep("=", 100), "\n\n")

# Define hybrid weights (green bond weight, treasury weight)
hybrid_weights <- list(
  "Hybrid_25_75" = c(green = 0.25, treasury = 0.75),
  "Hybrid_50_50" = c(green = 0.50, treasury = 0.50),
  "Hybrid_75_25" = c(green = 0.75, treasury = 0.25)
)

# Get list of green portfolios (exclude Treasury)
green_portfolios <- names(all_results)

# Store all hybrid results
all_hybrid_results <- list()

# Create hybrid portfolios for each green portfolio
for (green_port in green_portfolios) {
  
  cat("\n--- Creating hybrids for:", green_port, "---\n")
  
  # Get green portfolio data
  green_data <- all_results[[green_port]]$portfolio %>%
    dplyr::select(Date, Green_Value = Portfolio_Value)
  
  # Get treasury portfolio data
  treasury_data <- treasury_result$portfolio %>%
    dplyr::select(Date, Treasury_Value = Portfolio_Value)
  
  # Merge the two portfolios
  merged_data <- inner_join(green_data, treasury_data, by = "Date")
  
  # Create each hybrid combination
  for (hybrid_name in names(hybrid_weights)) {
    
    w_green <- hybrid_weights[[hybrid_name]]["green"]
    w_treasury <- hybrid_weights[[hybrid_name]]["treasury"]
    
    # Calculate hybrid portfolio value as convex combination
    hybrid_portfolio <- merged_data %>%
      mutate(
        Portfolio_Value = w_green * Green_Value + w_treasury * Treasury_Value,
        Portfolio = paste0(green_port, "_", hybrid_name)
      ) %>%
      dplyr::select(Date, Portfolio_Value, Portfolio)
    
    # Store results
    full_hybrid_name <- paste0(green_port, "_", hybrid_name)
    all_hybrid_results[[full_hybrid_name]] <- list(
      portfolio = hybrid_portfolio,
      weight_green = w_green,
      weight_treasury = w_treasury,
      base_green = green_port
    )
    
    cat("  Created:", full_hybrid_name, 
        sprintf("(%.0f%% green + %.0f%% treasury)\n", 
                w_green*100, w_treasury*100))
  }
}

cat("\nTotal hybrid portfolios created:", length(all_hybrid_results), "\n")
```

# ============================================================================
# CUMULATIVE RETURN PLOTS FOR HYBRID PORTFOLIOS (Fig 13)
# ============================================================================
```{r}


# Calculate consistent scales
all_hybrid_data <- data.frame()

# Get list of duration-based portfolios
duration_portfolios <- names(all_results)

for (group_port in duration_portfolios) {
  group_data <- all_results[[group_port]]$portfolio %>%
    mutate(Cumulative_Return = (Portfolio_Value / Portfolio_Value[1] - 1) * 100)
  all_hybrid_data <- rbind(all_hybrid_data, 
                           data.frame(Cumulative_Return = group_data$Cumulative_Return))
  
  for (hybrid_name in names(hybrid_weights)) {
    full_name <- paste0(group_port, "_", hybrid_name)
    hybrid_data <- all_hybrid_results[[full_name]]$portfolio %>%
      mutate(Cumulative_Return = (Portfolio_Value / Portfolio_Value[1] - 1) * 100)
    all_hybrid_data <- rbind(all_hybrid_data, 
                             data.frame(Cumulative_Return = hybrid_data$Cumulative_Return))
  }
}

treasury_data <- treasury_result$portfolio %>%
  mutate(Cumulative_Return = (Portfolio_Value / Portfolio_Value[1] - 1) * 100)
all_hybrid_data <- rbind(all_hybrid_data, 
                         data.frame(Cumulative_Return = treasury_data$Cumulative_Return))

y_range <- range(all_hybrid_data$Cumulative_Return, na.rm = TRUE)
y_padding <- diff(y_range) * 0.05
y_limits <- c(y_range[1] - y_padding, y_range[2] + y_padding)

cat("\n=== Y-axis limits:", round(y_limits[1], 2), "to", round(y_limits[2], 2), "===\n")

# Create color gradient: navy (0%) to lightgreen (100%)
color_gradient <- colorRampPalette(c("navy", "lightgreen"))(101)

# Plot hybrids for each duration-based portfolio
for (group_port in duration_portfolios) {
  
  cat("\n--- Plotting hybrids for:", group_port, "---\n")
  
  plot_data <- data.frame()
  
  # Add pure duration-based portfolio (100%)
  group_data <- all_results[[group_port]]$portfolio %>%
    mutate(
      Cumulative_Return = (Portfolio_Value / Portfolio_Value[1] - 1) * 100,
      Portfolio_Type = paste0(group_port, " (100%)"),
      Group_Pct = 100
    ) %>%
    dplyr::select(Date, Cumulative_Return, Portfolio_Type, Group_Pct)
  plot_data <- rbind(plot_data, group_data)
  
  # Add hybrid portfolios
  for (hybrid_name in names(hybrid_weights)) {
    full_name <- paste0(group_port, "_", hybrid_name)
    w_group <- hybrid_weights[[hybrid_name]]["green"]  # Using same weight structure
    
    hybrid_data <- all_hybrid_results[[full_name]]$portfolio %>%
      mutate(
        Cumulative_Return = (Portfolio_Value / Portfolio_Value[1] - 1) * 100,
        Portfolio_Type = sprintf("%s (%.0f%%)", group_port, w_group*100),
        Group_Pct = w_group * 100
      ) %>%
      dplyr::select(Date, Cumulative_Return, Portfolio_Type, Group_Pct)
    plot_data <- rbind(plot_data, hybrid_data)
  }
  
  # Add pure Treasury (0%)
  treasury_data <- treasury_result$portfolio %>%
    mutate(
      Cumulative_Return = (Portfolio_Value / Portfolio_Value[1] - 1) * 100,
      Portfolio_Type = "Treasury (0%)",
      Group_Pct = 0
    ) %>%
    dplyr::select(Date, Cumulative_Return, Portfolio_Type, Group_Pct)
  plot_data <- rbind(plot_data, treasury_data)
  
  # Get unique portfolio types and assign colors based on group percentage
  unique_portfolios <- plot_data %>%
    dplyr::select(Portfolio_Type, Group_Pct) %>%
    distinct() %>%
    arrange(desc(Group_Pct))
  
  # Assign colors from gradient based on group percentage
  portfolio_colors <- sapply(unique_portfolios$Group_Pct, function(pct) {
    color_gradient[round(pct) + 1]  # +1 because index starts at 1
  })
  names(portfolio_colors) <- unique_portfolios$Portfolio_Type
  
  # Assign linetypes (Treasury dashed, others solid)
  portfolio_linetypes <- ifelse(unique_portfolios$Group_Pct == 0, "dashed", "solid")
  names(portfolio_linetypes) <- unique_portfolios$Portfolio_Type
  
  # Create plot
  p <- ggplot(plot_data, aes(x = Date, y = Cumulative_Return, 
                              color = Portfolio_Type, linetype = Portfolio_Type)) +
    geom_hline(yintercept = 0, color = "gray50", linetype = "dotted", size = 0.5) +
    geom_line(size = 1.1) +
    scale_color_manual(
      values = portfolio_colors,
      name = "Portfolio"
    ) +
    scale_linetype_manual(
      values = portfolio_linetypes,
      name = "Portfolio"
    ) +
    coord_cartesian(ylim = y_limits) +
    scale_y_continuous(
      breaks = seq(floor(y_limits[1]/5)*5, ceiling(y_limits[2]/5)*5, by = 5)
    ) +
    labs(
      #title = paste("Duration-Based Portfolio:", group_port),
      #subtitle = "Cumulative returns for hybrid portfolios (100% / 75% / 50% / 25% / 0% Duration-Based)",
      x = "Date",
      y = "Cumulative Return (%)"
    ) +
    theme_minimal() +
    theme(
      plot.title = element_text(face = "bold", size = 14, hjust = 0.5),
      plot.subtitle = element_text(size = 11, hjust = 0.5),
      legend.position = "bottom",
      legend.title = element_text(face = "bold", size = 11),
      legend.text = element_text(size = 10),
      panel.border = element_rect(color = "black", fill = NA, linewidth = 0.8),
      panel.grid.major = element_line(color = "grey90", linewidth = 0.3),
      panel.grid.minor = element_blank(),
      axis.text = element_text(size = 10),
      axis.title = element_text(size = 11, face = "bold")
    ) +
    guides(
      color = guide_legend(nrow = 2, override.aes = list(size = 1.5)),
      linetype = guide_legend(nrow = 2)
    )
  
  print(p)
}
```


# ============================================================================
# PERFORMANCE METRICS FOR HYBRID PORTFOLIOS
# ============================================================================
```{r}

# Calculate performance metrics for all hybrid portfolios
hybrid_performance_overall <- data.frame()
hybrid_performance_yearly <- list()

for (yr in c(years, "Overall")) {
  hybrid_performance_yearly[[as.character(yr)]] <- data.frame()
}

risk_free_rate_pct <- 1.0  # 1% annual

for (full_name in names(all_hybrid_results)) {
  
  hybrid_portfolio <- all_hybrid_results[[full_name]]$portfolio
  
  # Overall metrics - use existing calc_performance_metrics function
  metrics_overall <- calc_performance_metrics(
    hybrid_portfolio$Portfolio_Value,
    hybrid_portfolio$Date,
    risk_free_rate_pct / 100  # Convert to decimal (0.01)
  )
  
  hybrid_performance_overall <- rbind(hybrid_performance_overall, data.frame(
    Portfolio = full_name,
    Total_Return_Pct = metrics_overall$Total_Return_Pct,
    Sharpe_Ratio = metrics_overall$Sharpe_Ratio,
    Sortino_Ratio = metrics_overall$Sortino_Ratio,
    Max_Drawdown_Pct = metrics_overall$Max_Drawdown_Pct,
    Ann_Volatility = metrics_overall$Ann_Volatility,
    Base_Green = all_hybrid_results[[full_name]]$base_green,
    Green_Weight = all_hybrid_results[[full_name]]$weight_green
  ))
  
  # Yearly metrics
  hybrid_portfolio_year <- hybrid_portfolio %>%
    mutate(Year = year(Date))
  
  for (yr in years) {
    year_data <- hybrid_portfolio_year %>% filter(Year == yr)
    
    if (nrow(year_data) > 1) {
      # Use existing calc_performance_metrics function
      metrics_yearly <- calc_performance_metrics(
        year_data$Portfolio_Value,
        year_data$Date,
        risk_free_rate_pct / 100  # Convert to decimal (0.01)
      )
      
      hybrid_performance_yearly[[as.character(yr)]] <- rbind(
        hybrid_performance_yearly[[as.character(yr)]],
        data.frame(
          Portfolio = full_name,
          Year = yr,
          Total_Return_Pct = metrics_yearly$Total_Return_Pct,
          Sharpe_Ratio = metrics_yearly$Sharpe_Ratio,
          Sortino_Ratio = metrics_yearly$Sortino_Ratio,
          Max_Drawdown_Pct = metrics_yearly$Max_Drawdown_Pct,
          Ann_Volatility = metrics_yearly$Ann_Volatility,
          Base_Green = all_hybrid_results[[full_name]]$base_green,
          Green_Weight = all_hybrid_results[[full_name]]$weight_green
        )
      )
    }
  }
}

# Display overall performance
cat("\n\n", rep("=", 100), "\n")
cat("HYBRID PORTFOLIO PERFORMANCE - OVERALL\n")
cat(rep("=", 100), "\n\n")

hybrid_performance_overall_display <- hybrid_performance_overall %>%
  arrange(Base_Green, desc(Green_Weight)) %>%
  dplyr::select(Portfolio, Green_Weight, Total_Return_Pct, Sharpe_Ratio, 
         Sortino_Ratio, Max_Drawdown_Pct, Ann_Volatility)

print(hybrid_performance_overall_display, row.names = FALSE)
```

# ============================================================================
# COMPARISON TABLES: HYBRIDS VS PURE PORTFOLIOS
# ============================================================================
```{r}

# For each green portfolio, create comparison table with its hybrids
for (green_port in green_portfolios) {
  
  cat("\n\n", rep("=", 80), "\n")
  cat("PERFORMANCE COMPARISON:", green_port, "\n")
  cat(rep("=", 80), "\n\n")
  
  # Collect relevant portfolios
  comparison_portfolios <- c(
    green_port,
    paste0(green_port, "_Hybrid_75_25"),
    paste0(green_port, "_Hybrid_50_50"),
    paste0(green_port, "_Hybrid_25_75"),
    "Treasury"
  )
  
  # Build comparison table
  comp_table <- data.frame()
  
  for (port in comparison_portfolios) {
    if (port == "Treasury") {
      # Treasury data
      metrics <- performance_metrics_overall %>% filter(Portfolio == "Treasury")
      green_pct <- 0
    } else if (port == green_port) {
      # Pure green
      metrics <- performance_metrics_overall %>% filter(Portfolio == green_port)
      green_pct <- 100
    } else {
      # Hybrid
      metrics <- hybrid_performance_overall %>% filter(Portfolio == port)
      green_pct <- metrics$Green_Weight * 100
    }
    
    comp_table <- rbind(comp_table, data.frame(
      Portfolio = port,
      Green_Pct = green_pct,
      Return = metrics$Total_Return_Pct,
      Sharpe = metrics$Sharpe_Ratio,
      Sortino = metrics$Sortino_Ratio,
      Max_DD = metrics$Max_Drawdown_Pct,
      Volatility = metrics$Ann_Volatility
    ))
  }
  
  print(comp_table, row.names = FALSE, digits = 3)
}
```

# ============================================================================
# YEARLY PERFORMANCE TABLES FOR HYBRIDS
# ============================================================================
```{r}

for (green_port in green_portfolios) {
  
  cat("\n\n", rep("=", 80), "\n")
  cat("YEARLY PERFORMANCE:", green_port, "HYBRIDS\n")
  cat(rep("=", 80), "\n\n")
  
  # Collect relevant portfolios
  comparison_portfolios <- c(
    green_port,
    paste0(green_port, "_Hybrid_75_25"),
    paste0(green_port, "_Hybrid_50_50"),
    paste0(green_port, "_Hybrid_25_75"),
    "Treasury"
  )
  
  # Create yearly table
  for (yr in years) {
    cat("\n--- Year:", yr, "---\n")
    
    yearly_comp <- data.frame()
    
    for (port in comparison_portfolios) {
      
      # Get the appropriate metrics
      if (port == "Treasury") {
        metrics <- performance_metrics_yearly[[as.character(yr)]] %>% 
          filter(Portfolio == "Treasury")
        w_green <- 0
      } else if (port == green_port) {
        metrics <- performance_metrics_yearly[[as.character(yr)]] %>% 
          filter(Portfolio == green_port)
        w_green <- 100
      } else {
        metrics <- hybrid_performance_yearly[[as.character(yr)]] %>% 
          filter(Portfolio == port)
        
        # Get green weight from hybrid results
        if (port %in% names(all_hybrid_results)) {
          w_green <- all_hybrid_results[[port]]$weight_green * 100
        } else {
          w_green <- NA
        }
      }
      
      # Only add row if we have valid data with all required columns
      if (nrow(metrics) > 0 && 
          !is.null(metrics$Total_Return_Pct) && 
          !is.null(metrics$Sharpe_Ratio) &&
          !is.null(metrics$Sortino_Ratio) &&
          !is.null(metrics$Max_Drawdown_Pct) &&
          !is.null(metrics$Ann_Volatility)) {
        
        yearly_comp <- rbind(yearly_comp, data.frame(
          Portfolio = port,
          Green_Pct = w_green,
          Return = as.numeric(metrics$Total_Return_Pct[1]),
          Sharpe = as.numeric(metrics$Sharpe_Ratio[1]),
          Sortino = as.numeric(metrics$Sortino_Ratio[1]),
          Max_DD = as.numeric(metrics$Max_Drawdown_Pct[1]),
          Volatility = as.numeric(metrics$Ann_Volatility[1]),
          stringsAsFactors = FALSE
        ))
      }
    }
    
    if (nrow(yearly_comp) > 0) {
      print(yearly_comp, row.names = FALSE, digits = 3)
    } else {
      cat("  No data available for this year.\n")
    }
  }
}
```

# ============================================================================
# LATEX TABLE FOR HYBRIDS (Table 8)
# ============================================================================
```{r}


for (dur_port in duration_portfolios) {
  
  cat("\n\n", rep("=", 100), "\n")
  cat("LATEX TABLE FOR:", dur_port, "DURATION-BASED HYBRIDS\n")
  cat(rep("=", 100), "\n\n")
  
  # Portfolio names
  portfolios_for_table <- c(
    dur_port,
    paste0(dur_port, "_Hybrid_75_25"),
    paste0(dur_port, "_Hybrid_50_50"),
    paste0(dur_port, "_Hybrid_25_75"),
    "Treasury"
  )
  
  portfolio_labels <- c(
    paste0(dur_port, " (100\\% Duration-Based)"),
    paste0(dur_port, " (75\\% Duration-Based)"),
    paste0(dur_port, " (50\\% Duration-Based)"),
    paste0(dur_port, " (25\\% Duration-Based)"),
    "Treasury (0\\% Duration-Based)"
  )
  
  # Initialize table
  latex_duration_table <- data.frame(Portfolio = portfolio_labels)
  
  # Add yearly columns
  for (yr in years) {
    yearly_data_pure <- performance_metrics_yearly[[as.character(yr)]]
    yearly_data_hybrid <- hybrid_performance_yearly[[as.character(yr)]]
    
    for (metric in c("Return", "Sharpe", "Sortino", "MaxDD")) {
      col_name <- paste0(metric, "_", yr)
      
      latex_duration_table[[col_name]] <- sapply(1:length(portfolios_for_table), function(i) {
        port <- portfolios_for_table[i]
        
        if (port == "Treasury" || port == dur_port) {
          idx <- which(yearly_data_pure$Portfolio == port)
          if (length(idx) > 0) {
            if (metric == "Return") return(yearly_data_pure$Total_Return_Pct[idx])
            if (metric == "Sharpe") return(yearly_data_pure$Sharpe_Ratio[idx])
            if (metric == "Sortino") return(yearly_data_pure$Sortino_Ratio[idx])
            if (metric == "MaxDD") return(yearly_data_pure$Max_Drawdown_Pct[idx])
          }
        } else {
          idx <- which(yearly_data_hybrid$Portfolio == port)
          if (length(idx) > 0) {
            if (metric == "Return") return(yearly_data_hybrid$Total_Return_Pct[idx])
            if (metric == "Sharpe") return(yearly_data_hybrid$Sharpe_Ratio[idx])
            if (metric == "Sortino") return(yearly_data_hybrid$Sortino_Ratio[idx])
            if (metric == "MaxDD") return(yearly_data_hybrid$Max_Drawdown_Pct[idx])
          }
        }
        return(NA)
      })
    }
  }
  
  # Add overall columns
  overall_data_pure <- performance_metrics_overall
  overall_data_hybrid <- hybrid_performance_overall
  
  for (metric in c("Return", "Sharpe", "Sortino", "MaxDD")) {
    col_name <- paste0(metric, "_Overall")
    
    latex_duration_table[[col_name]] <- sapply(1:length(portfolios_for_table), function(i) {
      port <- portfolios_for_table[i]
      
      if (port == "Treasury" || port == dur_port) {
        idx <- which(overall_data_pure$Portfolio == port)
        if (length(idx) > 0) {
          if (metric == "Return") return(overall_data_pure$Total_Return_Pct[idx])
          if (metric == "Sharpe") return(overall_data_pure$Sharpe_Ratio[idx])
          if (metric == "Sortino") return(overall_data_pure$Sortino_Ratio[idx])
          if (metric == "MaxDD") return(overall_data_pure$Max_Drawdown_Pct[idx])
        }
      } else {
        idx <- which(overall_data_hybrid$Portfolio == port)
        if (length(idx) > 0) {
          if (metric == "Return") return(overall_data_hybrid$Total_Return_Pct[idx])
          if (metric == "Sharpe") return(overall_data_hybrid$Sharpe_Ratio[idx])
          if (metric == "Sortino") return(overall_data_hybrid$Sortino_Ratio[idx])
          if (metric == "MaxDD") return(overall_data_hybrid$Max_Drawdown_Pct[idx])
        }
      }
      return(NA)
    })
  }
  
  # Generate LaTeX output
  cat("\\begin{table}[htbp]\n")
  cat("\\centering\n")
  cat(sprintf("\\caption{Hybrid Portfolio Performance: %s (10-Year Duration Target, 2020--2024)}\n", dur_port))
  cat(sprintf("\\label{tab:hybrid_duration_%s}\n", tolower(gsub(" ", "_", dur_port))))
  cat("\\resizebox{\\textwidth}{!}{\n")
  cat("\\begin{tabular}{l", paste(rep("r", ncol(latex_duration_table) - 1), collapse = ""), "}\n")
  cat("\\hline\\hline\n")
  
  # Headers
  header1 <- "Portfolio"
  for (yr in years) {
    header1 <- paste0(header1, " & \\multicolumn{4}{c}{", yr, "}")
  }
  header1 <- paste0(header1, " & \\multicolumn{4}{c}{Overall} \\\\\n")
  cat(header1)
  
  header2 <- " "
  for (yr in c(years, "Overall")) {
    header2 <- paste0(header2, " & Return & Sharpe & Sortino & Max DD")
  }
  header2 <- paste0(header2, " \\\\\n")
  cat(header2)
  
  header3 <- " "
  for (yr in c(years, "Overall")) {
    header3 <- paste0(header3, " & (\\%) & & & (\\%)")
  }
  header3 <- paste0(header3, " \\\\\n")
  cat(header3)
  cat("\\hline\n")
  
  # Data rows (3 decimal places)
  for (i in 1:nrow(latex_duration_table)) {
    row_str <- latex_duration_table$Portfolio[i]
    
    for (yr in years) {
      ret <- sprintf("%.3f", latex_duration_table[[paste0("Return_", yr)]][i])
      sha <- sprintf("%.3f", latex_duration_table[[paste0("Sharpe_", yr)]][i])
      sor <- sprintf("%.3f", latex_duration_table[[paste0("Sortino_", yr)]][i])
      mdd <- sprintf("%.3f", latex_duration_table[[paste0("MaxDD_", yr)]][i])
      row_str <- paste0(row_str, " & ", ret, " & ", sha, " & ", sor, " & ", mdd)
    }
    
    # Overall (3 decimal)
    ret_ov <- sprintf("%.3f", latex_duration_table$Return_Overall[i])
    sha_ov <- sprintf("%.3f", latex_duration_table$Sharpe_Overall[i])
    sor_ov <- sprintf("%.3f", latex_duration_table$Sortino_Overall[i])
    mdd_ov <- sprintf("%.3f", latex_duration_table$MaxDD_Overall[i])
    row_str <- paste0(row_str, " & ", ret_ov, " & ", sha_ov, " & ", sor_ov, " & ", mdd_ov)
    
    cat(row_str, " \\\\\n")
  }
  
  cat("\\hline\\hline\n")
  cat("\\end{tabular}\n")
  cat("}\n")
  cat("\\end{table}\n\n")
}


```


# ============================================================================
# PREPARE COMBINED RETURNS DATA FOR HYBRID ANALYSIS
# ============================================================================
```{r}

# Combine all returns data: pure portfolios + hybrids + treasury
combined_returns <- data.frame()

# Add pure duration-based portfolios (100%)
for (green_port in green_portfolios) {
  portfolio_data <- all_results[[green_port]]$portfolio %>%
    mutate(Year = year(Date))
  
  # Yearly data
  for (yr in years) {
    year_data <- portfolio_data %>% filter(Year == yr)
    if (nrow(year_data) > 1) {
      daily_returns <- calc_daily_returns(year_data$Portfolio_Value)
      combined_returns <- rbind(combined_returns, data.frame(
        Portfolio = green_port,
        Year = as.character(yr),
        Daily_Return = daily_returns,
        Base_Green = green_port,
        Green_Weight = 1.0
      ))
    }
  }
  
  # Overall data
  daily_returns_overall <- calc_daily_returns(portfolio_data$Portfolio_Value)
  combined_returns <- rbind(combined_returns, data.frame(
    Portfolio = green_port,
    Year = "Overall",
    Daily_Return = daily_returns_overall,
    Base_Green = green_port,
    Green_Weight = 1.0
  ))
}

# Add hybrid portfolios
for (full_name in names(all_hybrid_results)) {
  hybrid_info <- all_hybrid_results[[full_name]]
  
  portfolio_data <- hybrid_info$portfolio %>%
    mutate(Year = year(Date))
  
  # Yearly data
  for (yr in years) {
    year_data <- portfolio_data %>% filter(Year == yr)
    if (nrow(year_data) > 1) {
      daily_returns <- calc_daily_returns(year_data$Portfolio_Value)
      combined_returns <- rbind(combined_returns, data.frame(
        Portfolio = full_name,
        Year = as.character(yr),
        Daily_Return = daily_returns,
        Base_Green = hybrid_info$base_green,
        Green_Weight = hybrid_info$weight_green
      ))
    }
  }
  
  # Overall data
  daily_returns_overall <- calc_daily_returns(portfolio_data$Portfolio_Value)
  combined_returns <- rbind(combined_returns, data.frame(
    Portfolio = full_name,
    Year = "Overall",
    Daily_Return = daily_returns_overall,
    Base_Green = hybrid_info$base_green,
    Green_Weight = hybrid_info$weight_green
  ))
}

# Add Treasury (0%)
treasury_data_year <- treasury_result$portfolio %>%
  mutate(Year = year(Date))

for (yr in years) {
  year_data <- treasury_data_year %>% filter(Year == yr)
  if (nrow(year_data) > 1) {
    daily_returns <- calc_daily_returns(year_data$Portfolio_Value)
    combined_returns <- rbind(combined_returns, data.frame(
      Portfolio = "Treasury",
      Year = as.character(yr),
      Daily_Return = daily_returns,
      Base_Green = NA,
      Green_Weight = 0
    ))
  }
}

# Overall Treasury
daily_returns_treasury_overall <- calc_daily_returns(treasury_result$portfolio$Portfolio_Value)
combined_returns <- rbind(combined_returns, data.frame(
  Portfolio = "Treasury",
  Year = "Overall",
  Daily_Return = daily_returns_treasury_overall,
  Base_Green = NA,
  Green_Weight = 0
))

# Set Year factor levels
year_levels <- c(as.character(years), "Overall")
combined_returns$Year <- factor(combined_returns$Year, levels = year_levels)

cat("\n=== Combined Returns Data Created ===\n")
cat("Total rows:", nrow(combined_returns), "\n")
cat("Portfolios included:", length(unique(combined_returns$Portfolio)), "\n")
cat("Years:", paste(unique(combined_returns$Year), collapse = ", "), "\n\n")

```

# ============================================================================
# BOX PLOTS FOR DURATION-BASED HYBRID PORTFOLIOS (Fig 14)
# ============================================================================
```{r}

# Calculate consistent y-axis limits
all_hybrid_returns <- combined_returns %>%
  filter(!is.na(Daily_Return))

y_range_hybrid <- range(all_hybrid_returns$Daily_Return, na.rm = TRUE)
y_padding_hybrid <- diff(y_range_hybrid) * 0.05
y_limits_hybrid <- c(y_range_hybrid[1] - y_padding_hybrid, y_range_hybrid[2] + y_padding_hybrid)

cat("\n=== Y-axis limits:", round(y_limits_hybrid[1], 2), "to", round(y_limits_hybrid[2], 2), "===\n\n")

# Create box plots for each duration-based portfolio
for (green_port in green_portfolios) {
  
  cat("\n--- Box plots for:", green_port, "---\n")
  
  # Filter data
  box_data_all <- combined_returns %>%
    filter(Base_Green == green_port | Portfolio == "Treasury") %>%
    mutate(
      Portfolio_Label = case_when(
        Portfolio == "Treasury" ~ "Treasury\n(0%)",
        Green_Weight == 1.0 ~ paste0(green_port, "\n(100%)"),
        TRUE ~ sprintf("%s\n(%.0f%%)", green_port, Green_Weight * 100)
      ),
      Portfolio_Label = factor(Portfolio_Label, 
                               levels = unique(Portfolio_Label[order(-Green_Weight)])),
      # Green percentage for color mapping
      Green_Pct = case_when(
        Portfolio == "Treasury" ~ 0,
        TRUE ~ Green_Weight * 100
      )
    )
  
  # Create color gradient matching your scale: navy (0%) to lightgreen (100%)
  color_gradient <- colorRampPalette(c("navy", "lightgreen"))(101)  # 0-100%
  
  # Get unique portfolios and assign colors based on green percentage
  unique_portfolios <- box_data_all %>%
    dplyr::select(Portfolio_Label, Green_Pct) %>%
    distinct() %>%
    arrange(desc(Green_Pct))
  
  # Map colors based on green percentage
  hybrid_colors <- sapply(unique_portfolios$Green_Pct, function(pct) {
    color_gradient[round(pct) + 1]  # +1 because index starts at 1
  })
  names(hybrid_colors) <- unique_portfolios$Portfolio_Label
  
  # Set Year factor levels
  year_levels <- c(as.character(years), "Overall")
  box_data_all$Year <- factor(box_data_all$Year, levels = year_levels)
  
  # -------------------------------------------------------------------------
  # PLOT 1: Yearly + Overall in facets
  # -------------------------------------------------------------------------
  p_box_with_overall <- ggplot(box_data_all, aes(x = Portfolio_Label, y = Daily_Return, 
                                                   fill = Portfolio_Label)) +
    geom_boxplot(outlier.size = 0.5, outlier.alpha = 0.3) +
    facet_wrap(~ Year, nrow = 1) +
    scale_fill_manual(values = hybrid_colors) +
    coord_cartesian(ylim = y_limits_hybrid) +
    labs(
      #title = paste("Daily Return Distribution (Yearly + Overall):", green_port, "Hybrids"),
      x = "Portfolio",
      y = "Daily Return (%)"
    ) +
    theme_minimal() +
    theme(
      plot.title = element_text(face = "bold", size = 12, hjust = 0.5),
      legend.position = "none",
      axis.text.x = element_text(angle = 45, hjust = 1, size = 5),
      axis.title = element_text(size = 11, face = "bold"),
      strip.text = element_text(face = "bold", size = 9),
      panel.border = element_rect(color = "black", fill = NA, linewidth = 0.6),
      panel.grid.major = element_line(color = "grey90"),
      panel.grid.minor = element_blank(),
      plot.background = element_rect(color = "black", fill = NA, linewidth = 1),
      panel.spacing = unit(0.5, "lines")
    )
  
  print(p_box_with_overall)
  
  # -------------------------------------------------------------------------
  # PLOT 2: Overall only
  # -------------------------------------------------------------------------
  box_data_overall <- box_data_all %>% filter(Year == "Overall")
  
  p_box_overall_only <- ggplot(box_data_overall, aes(x = Portfolio_Label, y = Daily_Return, 
                                                       fill = Portfolio_Label)) +
    geom_boxplot(outlier.size = 1, outlier.alpha = 0.4, width = 0.6) +
    stat_summary(fun = mean, geom = "point", shape = 23, size = 3, 
                 fill = "white", color = "black") +
    scale_fill_manual(values = hybrid_colors) +
    coord_cartesian(ylim = y_limits_hybrid) +
    labs(
      title = paste("Overall Daily Return Distribution:", green_port, "Hybrids"),
      subtitle = "Diamond marks represent mean returns",
      x = "Portfolio",
      y = "Daily Return (%)"
    ) +
    theme_minimal() +
    theme(
      plot.title = element_text(face = "bold", size = 14, hjust = 0.5),
      plot.subtitle = element_text(size = 11, hjust = 0.5),
      legend.position = "none",
      axis.text.x = element_text(angle = 45, hjust = 1, size = 10),
      axis.title = element_text(size = 12, face = "bold"),
      panel.border = element_rect(color = "black", fill = NA, linewidth = 0.8),
      panel.grid.major = element_line(color = "grey90"),
      panel.grid.minor = element_blank()
    )
  
  print(p_box_overall_only)
}
```

# ============================================================================
# RISK-RETURN SCATTER PLOT FOR HYBRIDS (Fig 15)
# ============================================================================
```{r fig.width=12, fig.height=8}

library(ggrepel)

# Calculate consistent scales
all_scatter_data <- data.frame()

for (green_port in green_portfolios) {
  comparison_portfolios <- c(
    green_port,
    paste0(green_port, "_Hybrid_75_25"),
    paste0(green_port, "_Hybrid_50_50"),
    paste0(green_port, "_Hybrid_25_75"),
    "Treasury"
  )
  
  for (port in comparison_portfolios) {
    if (port == "Treasury") {
      metrics <- performance_metrics_overall %>% filter(Portfolio == "Treasury")
      green_pct <- 0
      returns <- calc_daily_returns(treasury_result$portfolio$Portfolio_Value)
    } else if (port == green_port) {
      metrics <- performance_metrics_overall %>% filter(Portfolio == green_port)
      green_pct <- 100
      returns <- calc_daily_returns(all_results[[green_port]]$portfolio$Portfolio_Value)
    } else {
      metrics <- hybrid_performance_overall %>% filter(Portfolio == port)
      green_pct <- metrics$Green_Weight * 100
      returns <- calc_daily_returns(all_hybrid_results[[port]]$portfolio$Portfolio_Value)
    }
    
    volatility <- sd(returns, na.rm = TRUE) * sqrt(252) * 100
    
    all_scatter_data <- rbind(all_scatter_data, data.frame(
      Green_Portfolio = green_port,
      Return = metrics$Total_Return_Pct,
      Volatility = volatility,
      Green_Pct = green_pct,
      Sharpe = metrics$Sharpe_Ratio
    ))
  }
}

vol_range <- range(all_scatter_data$Volatility, na.rm = TRUE)
ret_range <- range(all_scatter_data$Return, na.rm = TRUE)
vol_padding <- diff(vol_range) * 0.1
ret_padding <- diff(ret_range) * 0.1
vol_limits <- c(vol_range[1] - vol_padding, vol_range[2] + vol_padding)
ret_limits <- c(ret_range[1] - ret_padding, ret_range[2] + ret_padding)

# Create plots with compact legends
for (green_port in green_portfolios) {
  
  cat("\n--- Risk-return scatter for:", green_port, "---\n")
  
  comparison_portfolios <- c(
    green_port,
    paste0(green_port, "_Hybrid_75_25"),
    paste0(green_port, "_Hybrid_50_50"),
    paste0(green_port, "_Hybrid_25_75"),
    "Treasury"
  )
  
  scatter_data <- data.frame()
  
  for (port in comparison_portfolios) {
    if (port == "Treasury") {
      metrics <- performance_metrics_overall %>% filter(Portfolio == "Treasury")
      green_pct <- 0
      label <- "Treasury (0%)"
    } else if (port == green_port) {
      metrics <- performance_metrics_overall %>% filter(Portfolio == green_port)
      green_pct <- 100
      label <- paste0(green_port, " (100%)")
    } else {
      metrics <- hybrid_performance_overall %>% filter(Portfolio == port)
      green_pct <- metrics$Green_Weight * 100
      label <- sprintf("%s (%.0f%%)", green_port, green_pct)
    }
    
    if (port == "Treasury") {
      returns <- calc_daily_returns(treasury_result$portfolio$Portfolio_Value)
    } else if (port == green_port) {
      returns <- calc_daily_returns(all_results[[green_port]]$portfolio$Portfolio_Value)
    } else {
      returns <- calc_daily_returns(all_hybrid_results[[port]]$portfolio$Portfolio_Value)
    }
    
    volatility <- sd(returns, na.rm = TRUE) * sqrt(252) * 100
    
    scatter_data <- rbind(scatter_data, data.frame(
      Portfolio = label,
      Return = metrics$Total_Return_Pct,
      Volatility = volatility,
      Green_Pct = green_pct,
      Sharpe = metrics$Sharpe_Ratio
    ))
  }
  
  # Plot with COMPACT legends
  p_scatter <- ggplot(scatter_data, aes(x = Volatility, y = Return, 
                                        color = Green_Pct, size = Sharpe)) +
    geom_point(alpha = 0.8) +
    geom_label_repel(
      aes(label = Portfolio), 
      size = 3.5,
      box.padding = 0.8,
      point.padding = 0.5,
      segment.color = "grey50",
      segment.size = 0.3,
      max.overlaps = 20,
      show.legend = FALSE,
      force = 2,
      min.segment.length = 0,
      fill = alpha("white", 0.9),
      label.padding = unit(0.25, "lines")
    ) +
    scale_color_gradient(
      low = "navy", 
      high = "lightgreen", 
      name = "Green %",
      breaks = c(0, 25, 50, 75, 100)
    ) +
    scale_size_continuous(
      range = c(3, 12), 
      name = "Sharpe Ratio"
    ) +
    coord_cartesian(xlim = vol_limits, ylim = ret_limits) +
    labs(
      #title = paste("Risk-Return Profile:", green_port, "Hybrids"),
      #subtitle = "Point size represents Sharpe ratio",
      x = "Volatility (Annualized %)",
      y = "Total Return (%)"
    ) +
    # Compact legend styling
    guides(
      color = guide_colorbar(
        barwidth = 1.2,        # Narrower color bar
        barheight = 8,         # Shorter height
        title.position = "top",
        title.hjust = 0.5,
        label.position = "right"
      ),
      size = guide_legend(
        title.position = "top",
        title.hjust = 0.5,
        nrow = 4,              # Stack size legend vertically
        byrow = TRUE,
        override.aes = list(alpha = 0.8)
      )
    ) +
    theme_minimal() +
    theme(
      plot.title = element_text(face = "bold", size = 14),
      plot.subtitle = element_text(size = 11),
      legend.position = "right",
      legend.box = "vertical",
      legend.spacing = unit(0.3, "cm"),
      # Smaller legend text
      legend.title = element_text(size = 9, face = "bold"),
      legend.text = element_text(size = 8),
      # Smaller legend keys
      legend.key.size = unit(0.4, "cm"),
      legend.key.height = unit(0.4, "cm"),
      legend.key.width = unit(0.4, "cm"),
      # Margins
      legend.margin = margin(t = 0, r = 5, b = 0, l = 5),
      legend.box.spacing = unit(0.2, "cm"),
      panel.border = element_rect(color = "black", fill = NA, linewidth = 0.8),
      panel.grid.major = element_line(color = "grey90"),
      panel.grid.minor = element_line(color = "grey95")
    )
  
  print(p_scatter)
}
```

# ============================================================================
# SUMMARY STATISTICS TABLE FOR ALL HYBRIDS
# ============================================================================
```{r}

cat("\n\n", rep("=", 100), "\n")
cat("COMPREHENSIVE HYBRID PERFORMANCE SUMMARY\n")
cat(rep("=", 100), "\n\n")

# Combine all portfolios
all_performance <- rbind(
  performance_metrics_overall %>% 
    mutate(Green_Weight = ifelse(Portfolio == "Treasury", 0, 1),
           Base_Green = Portfolio) %>%
    dplyr::select(Portfolio, Base_Green, Green_Weight, Total_Return_Pct, 
           Sharpe_Ratio, Sortino_Ratio, Max_Drawdown_Pct, Ann_Volatility),
  hybrid_performance_overall %>%
    dplyr::select(Portfolio, Base_Green, Green_Weight, Total_Return_Pct, 
           Sharpe_Ratio, Sortino_Ratio, Max_Drawdown_Pct, Ann_Volatility)
)

# Sort by base portfolio and green weight
all_performance <- all_performance %>%
  arrange(Base_Green, desc(Green_Weight))

print(all_performance, row.names = FALSE, digits = 3)

# Summary by green weight level
cat("\n\n--- Performance by Green Weight Level ---\n\n")

weight_summary <- all_performance %>%
  group_by(Green_Weight) %>%
  summarize(
    N_Portfolios = n(),
    Avg_Return = mean(Total_Return_Pct, na.rm = TRUE),
    Avg_Sharpe = mean(Sharpe_Ratio, na.rm = TRUE),
    Avg_Sortino = mean(Sortino_Ratio, na.rm = TRUE),
    Avg_MaxDD = mean(Max_Drawdown_Pct, na.rm = TRUE),
    Avg_Volatility = mean(Ann_Volatility, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(Green_Pct = Green_Weight * 100) %>%
  dplyr::select(Green_Pct, everything(), -Green_Weight)

print(weight_summary, row.names = FALSE, digits = 3)
```

